---
title: "Utility of Normality Test in Two Samples Test"
author: "Benedict Kongyir"
date: "`r format(Sys.time(), '%m/%d/%Y')`"
output: 
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.height = 8, fig.width = 10)
source("~/Desktop/OSU/Research/Pretest-Simulation/functions/User_defined_functions.R")
source("~/Desktop/OSU/Research/Pretest-Simulation/functions/utility.R")


```


### Power loss and  Expected Power loss

#### At least one sample passed normality test

Power loss and expected power loss are prominent for smaller sample sizes(n less than 30), especially for skewed distributions like lognormal, exponential, but decreases to zero or close to zero as sample size increase( above 30).
```{r}
rm(list = ls())
load("/Users/benedictkongyir/Desktop/OSU/Research/Pretest-Simulation/Simulation/EXPECTED POWER LOSS/TWO SAMPLE/TWOSAMPLES-EXPECTED-POWERLOSS-ATLEAST-ONE-SAMPLE-PAST-NORMALITY.RData")
#Probability of SW test
data_prob_SW <-data.frame(prob.non.sig.SW.test_par)
# power loss
data_powerloss <-data.frame(powerloss)
#Expected powerloss
Expected_powerloss<-data_powerloss * data_prob_SW
```


```{r}
#par(mar = c(9, 4, 4, 1), xpd = TRUE)
par(mfrow = c(2,2))
# Adjust margins to reduce space between plots
par(mai = c(0.75, 0.75, 0.2, 0.2))  # Adjust as needed
plot(nvec, data_powerloss$Exponential,  type = "o", lty = 1, pch = 1, col = "red", lwd = 3, 
     ylim = c(-0.01, 0.1), xlim = range(nvec), xlab = "Sample Size", ylab = "Power Loss")
lines(nvec, data_powerloss$Weibull, type = "o", lty = 2, pch = 2, col = "blue", lwd = 3)
lines(nvec, data_powerloss$Chi.Square, type = "o", lty = 3, pch = 8, col = "green", lwd = 3)
lines(nvec, data_powerloss$LogNormal, type = "o", lty = 4, pch = 4, col = "orange", lwd = 3)
lines(nvec, data_powerloss$Gamma, type = "o", lty = 5, pch = 5, col = "purple", lwd = 3)
lines(nvec, data_powerloss$Pareto, type = "o", lty = 5, pch = 6, col = "grey", lwd = 3)
abline(h = 0, lwd = 2, col = "black", xpd = F)
title(main = "Power loss")
legend("topright", legend=c("Exp", "Weibull", "Chisq", "LogNormal", "Gamma", "Pareto"), lwd = 3,
       col=c("red", "blue", "green", "orange", "purple", "grey"), lty = 1:6, pch =c(1,2,8, 4,5, 6), cex = 0.8, title = "Distribution")

plot(nvec, data_powerloss$Laplace, type = "o", lty = 1, pch = 1, col = "red", lwd = 3, 
     ylim = c(-0.01, 0.1), xlim = range(nvec), xlab = "Sample Size", ylab = "Power Loss")
lines(nvec, data_powerloss$Standard.Normal, type = "o", lty = 2, pch = 2, col = "blue", lwd = 3)
lines(nvec, data_powerloss$t, type = "o", lty = 3, pch = 8, col = "green", lwd = 3)
lines(nvec, data_powerloss$Contaminated, type = "o", lty = 5, pch = 6, col = "grey", lwd = 3)
lines(nvec, data_powerloss$Uniform, type = "o", lty = 5, pch = 4, col = "purple", lwd = 3)
abline(h = 0, lwd = 2, col = "black", xpd = F)
title(main = "Power loss")
legend("topright", legend=c("Laplace", "Normal", "t", "Contaminated", "Uniform"), lwd = 3,
       col=c( "red", "blue", "green", "grey", "purple"), lty = 1:5,cex = 0.8, pch = c(1,2,8, 6, 4),title = "Distribution")

### Expected power loss
plot(nvec, Expected_powerloss$Exponential,  type = "o", lty = 1, pch = 1, col = "red", lwd = 3, 
     ylim = c(-0.01, 0.1), xlim = range(nvec), xlab = "Sample Size", ylab = "Expected Power Loss")
lines(nvec, Expected_powerloss$Weibull, type = "o", lty = 2, pch = 2, col = "blue", lwd = 3)
lines(nvec, Expected_powerloss$Chi.Square, type = "o", lty = 3, pch = 8, col = "green", lwd = 3)
lines(nvec, Expected_powerloss$LogNormal, type = "o", lty = 4, pch = 4, col = "orange", lwd = 3)
lines(nvec, Expected_powerloss$Gamma, type = "o", lty = 5, pch = 5, col = "purple", lwd = 3)
lines(nvec, data_powerloss$Pareto, type = "o", lty = 5, pch = 6, col = "grey", lwd = 3)
abline(h = 0, lwd = 2, col = "black", xpd = F)
title(main = "Expected Power loss")
legend("topright", legend=c("Exp", "Weibull", "Chisq", "LogNormal", "Gamma", "Pareto"), lwd = 3,
       col=c("red", "blue", "green", "orange", "purple", "grey"), lty = 1:6, pch =c(1,2,8, 4,5, 6), cex = 0.8, title = "Distribution")

plot(nvec, Expected_powerloss$Laplace, type = "o", lty = 1, pch = 1, col = "red", lwd = 3, 
     ylim = c(-0.01, 0.1), xlim = range(nvec), xlab = "Sample Size", ylab = "Expected Power Loss")
lines(nvec, Expected_powerloss$Standard.Normal, type = "o", lty = 2, pch = 2, col = "blue", lwd = 3)
lines(nvec, Expected_powerloss$t, type = "o", lty = 3, pch = 8, col = "green", lwd = 3)
lines(nvec, data_powerloss$Contaminated, type = "o", lty = 5, pch = 6, col = "grey", lwd = 3)
lines(nvec, data_powerloss$Uniform, type = "o", lty = 5, pch = 4, col = "purple", lwd = 3)
abline(h = 0, lwd = 2, col = "black", xpd = F)
title(main = "Expected Power loss")
legend("topright", legend=c("Laplace", "Normal", "t", "Contaminated", "Uniform"), lwd = 3,
       col=c( "red", "blue", "green", "grey", "purple"), lty = 1:5,cex = 0.8, pch = c(1,2,8, 6, 4), title = "Distribution")
```

### Power loss and  Expected Power loss

##### Both samples passed normality test


Power loss and expected power loss are minimal for almost all sample sizes except for sample sizes less than 10.
```{r}
rm(list = ls())
load("/Users/benedictkongyir/Desktop/OSU/Research/Pretest-Simulation/Simulation/EXPECTED POWER LOSS/TWO SAMPLE/TWOSAMPLES-POWERLOSS-BOTH-SAMPLES-PASSED-NORMALITY.RData")
#Probability of SW test
data_prob_SW <-data.frame(prob.non.sig.SW.test)
# power loss
data_powerloss <-data.frame(powerloss)
#Expected powerloss
Expected_powerloss<-data_powerloss * data_prob_SW
```


```{r}
#par(mar = c(9, 4, 4, 1), xpd = TRUE)
par(mfrow = c(2,2))
# Adjust margins to reduce space between plots
par(mai = c(0.75, 0.75, 0.2, 0.2))  # Adjust as needed
plot(nvec, data_powerloss$Exponential,  type = "o", lty = 1, pch = 1, col = "red", lwd = 3, 
     ylim = c(-0.01, 0.08), xlim = range(nvec), xlab = "Sample Size", ylab = "Power Loss")
lines(nvec, data_powerloss$Weibull, type = "o", lty = 2, pch = 2, col = "blue", lwd = 3)
lines(nvec, data_powerloss$Chi.Square, type = "o", lty = 3, pch = 8, col = "green", lwd = 3)
lines(nvec, data_powerloss$LogNormal, type = "o", lty = 4, pch = 4, col = "orange", lwd = 3)
lines(nvec, data_powerloss$Gamma, type = "o", lty = 5, pch = 5, col = "purple", lwd = 3)
lines(nvec, data_powerloss$Pareto, type = "o", lty = 5, pch = 6, col = "grey", lwd = 3)
abline(h = 0, lwd = 2, col = "black", xpd = F)
title(main = "Power loss")
legend("topright", legend=c("Exp", "Weibull", "Chisq", "LogNormal", "Gamma", "Pareto"), lwd = 3,
       col=c("red", "blue", "green", "orange", "purple", "grey"), lty = 1:6, pch =c(1,2,8, 4,5, 6), cex = 0.8, title = "Distribution")

plot(nvec, data_powerloss$Laplace, type = "o", lty = 1, pch = 1, col = "red", lwd = 3, 
     ylim = c(-0.01, 0.08), xlim = range(nvec), xlab = "Sample Size", ylab = "Power Loss")
lines(nvec, data_powerloss$Standard.Normal, type = "o", lty = 2, pch = 2, col = "blue", lwd = 3)
lines(nvec, data_powerloss$t, type = "o", lty = 3, pch = 8, col = "green", lwd = 3)
lines(nvec, data_powerloss$Contaminated, type = "o", lty = 5, pch = 6, col = "grey", lwd = 3)
lines(nvec, data_powerloss$Uniform, type = "o", lty = 5, pch = 4, col = "purple", lwd = 3)
abline(h = 0, lwd = 2, col = "black", xpd = F)
title(main = "Power loss")
legend("topright", legend=c("Laplace", "Normal", "t", "Contaminated", "Uniform"), lwd = 3,
       col=c( "red", "blue", "green", "grey", "purple"), lty = 1:5,cex = 0.8, pch = c(1,2,8, 6, 4),title = "Distribution")

### Expected power loss
plot(nvec, Expected_powerloss$Exponential,  type = "o", lty = 1, pch = 1, col = "red", lwd = 3, 
     ylim = c(-0.01, 0.08), xlim = range(nvec), xlab = "Sample Size", ylab = "Expected Power Loss")
lines(nvec, Expected_powerloss$Weibull, type = "o", lty = 2, pch = 2, col = "blue", lwd = 3)
lines(nvec, Expected_powerloss$Chi.Square, type = "o", lty = 3, pch = 8, col = "green", lwd = 3)
lines(nvec, Expected_powerloss$LogNormal, type = "o", lty = 4, pch = 4, col = "orange", lwd = 3)
lines(nvec, Expected_powerloss$Gamma, type = "o", lty = 5, pch = 5, col = "purple", lwd = 3)
lines(nvec, data_powerloss$Pareto, type = "o", lty = 5, pch = 6, col = "grey", lwd = 3)
abline(h = 0, lwd = 2, col = "black", xpd = F)
title(main = "Expected Power loss")
legend("topright", legend=c("Exp", "Weibull", "Chisq", "LogNormal", "Gamma", "Pareto"), lwd = 3,
       col=c("red", "blue", "green", "orange", "purple", "grey"), lty = 1:6, pch =c(1,2,8, 4,5, 6), cex = 0.8, title = "Distribution")

plot(nvec, Expected_powerloss$Laplace, type = "o", lty = 1, pch = 1, col = "red", lwd = 3, 
     ylim = c(-0.01, 0.08), xlim = range(nvec), xlab = "Sample Size", ylab = "Expected Power Loss")
lines(nvec, Expected_powerloss$Standard.Normal, type = "o", lty = 2, pch = 2, col = "blue", lwd = 3)
lines(nvec, Expected_powerloss$t, type = "o", lty = 3, pch = 8, col = "green", lwd = 3)
lines(nvec, data_powerloss$Contaminated, type = "o", lty = 5, pch = 6, col = "grey", lwd = 3)
lines(nvec, data_powerloss$Uniform, type = "o", lty = 5, pch = 4, col = "purple", lwd = 3)
abline(h = 0, lwd = 2, col = "black", xpd = F)
title(main = "Expected Power loss")
legend("topright", legend=c("Laplace", "Normal", "t", "Contaminated", "Uniform"), lwd = 3,
       col=c( "red", "blue", "green", "grey", "purple"), lty = 1:5,cex = 0.8, pch = c(1,2,8, 6, 4), title = "Distribution")
```



##### Power loss of Two Sample Two-Stage Procedure
```{r}
rm(list = ls())
load("/Users/benedictkongyir/Desktop/OSU/Research/Pretest-Simulation/Simulation/EXPECTED POWER LOSS/TWO SAMPLE/TWOSAMPLE.POWERLOSS.TWOSTAGE.PROCEDURE.RData")
#Probability of SW test
power.t.test <-data.frame(power_t_test_par)
# power loss
power.U.test <-data.frame(power_mann_whitney_par)
#Expected powerloss
overall_power<-data.frame(overall_power_par)
```


```{r, fig.width=10, fig.height=10}
#par(mar = c(9, 4, 4, 1), xpd = TRUE)
par(mfrow = c(3,2))
# Adjust margins to reduce space between plots
par(mai = c(0.75, 0.75, 0.2, 0.2))  # Adjust as needed
### overall power
plot(nvec, power.t.test$Exponential,  type = "o", lty = 1, pch = 1, col = "red", lwd = 3, 
     ylim = c(0, 1), xlim = range(nvec), xlab = "Sample Size", ylab = "power of t test")
lines(nvec, power.t.test$Weibull, type = "o", lty = 2, pch = 2, col = "blue", lwd = 3)
lines(nvec, power.t.test$Chi.Square, type = "o", lty = 3, pch = 8, col = "green", lwd = 3)
lines(nvec, power.t.test$LogNormal, type = "o", lty = 4, pch = 4, col = "orange", lwd = 3)
lines(nvec, power.t.test$Gamma, type = "o", lty = 5, pch = 5, col = "purple", lwd = 3)
lines(nvec, power.t.test$Pareto, type = "o", lty = 5, pch = 6, col = "grey", lwd = 3)
title(main = "power of t test")
legend("bottomright", legend=c("Exp", "Weibull", "Chisq", "LogNormal", "Gamma", "Pareto"), lwd = 3,
       col=c("red", "blue", "green", "orange", "purple", "grey"), lty = 1:6, pch =c(1,2,8, 4,5, 6), cex = 0.8, title = "Distribution")

plot(nvec, power.t.test$Laplace, type = "o", lty = 1, pch = 1, col = "red", lwd = 3, 
     ylim = c(-0, 1), xlim = range(nvec), xlab = "Sample Size", ylab = "power of t test")
lines(nvec, power.t.test$Standard.Normal, type = "o", lty = 2, pch = 2, col = "blue", lwd = 3)
lines(nvec, power.t.test$t, type = "o", lty = 3, pch = 8, col = "green", lwd = 3)
lines(nvec, power.t.test$Contaminated, type = "o", lty = 5, pch = 6, col = "grey", lwd = 3)
lines(nvec, power.t.test$Uniform, type = "o", lty = 5, pch = 4, col = "purple", lwd = 3)
title(main = "power of t test")
legend("topleft", legend=c("Laplace", "Normal", "t", "Contaminated", "Uniform"), lwd = 3,
       col=c( "red", "blue", "green", "grey", "purple"), lty = 1:5,cex = 0.8, pch = c(1,2,8, 6, 4), title = "Distribution")

plot(nvec, power.U.test$Exponential,  type = "o", lty = 1, pch = 1, col = "red", lwd = 3, 
     ylim = c(0, 1), xlim = range(nvec), xlab = "Sample Size", ylab = "power of U test")
lines(nvec, power.U.test$Weibull, type = "o", lty = 2, pch = 2, col = "blue", lwd = 3)
lines(nvec, power.U.test$Chi.Square, type = "o", lty = 3, pch = 8, col = "green", lwd = 3)
lines(nvec, power.U.test$LogNormal, type = "o", lty = 4, pch = 4, col = "orange", lwd = 3)
lines(nvec, power.U.test$Gamma, type = "o", lty = 5, pch = 5, col = "purple", lwd = 3)
lines(nvec, power.U.test$Pareto, type = "o", lty = 5, pch = 6, col = "grey", lwd = 3)
title(main = "power of U test")
legend("bottomright", legend=c("Exp", "Weibull", "Chisq", "LogNormal", "Gamma", "Pareto"), lwd = 3,
       col=c("red", "blue", "green", "orange", "purple", "grey"), lty = 1:6, pch =c(1,2,8, 4,5, 6), cex = 0.8, title = "Distribution")

plot(nvec, power.U.test$Laplace, type = "o", lty = 1, pch = 1, col = "red", lwd = 3, 
     ylim = c(-0, 1), xlim = range(nvec), xlab = "Sample Size", ylab = "power of U test")
lines(nvec, power.U.test$Standard.Normal, type = "o", lty = 2, pch = 2, col = "blue", lwd = 3)
lines(nvec, power.U.test$t, type = "o", lty = 3, pch = 8, col = "green", lwd = 3)
lines(nvec, power.U.test$Contaminated, type = "o", lty = 5, pch = 6, col = "grey", lwd = 3)
lines(nvec, power.U.test$Uniform, type = "o", lty = 5, pch = 4, col = "purple", lwd = 3)
title(main = "power of U test")
legend("topleft", legend=c("Laplace", "Normal", "t", "Contaminated", "Uniform"), lwd = 3,
       col=c( "red", "blue", "green", "grey", "purple"), lty = 1:5,cex = 0.8, pch = c(1,2,8, 6, 4), title = "Distribution")

plot(nvec, overall_power$Exponential,  type = "o", lty = 1, pch = 1, col = "red", lwd = 3, 
     ylim = c(0, 1), xlim = range(nvec), xlab = "Sample Size", ylab = "overall power of test")
lines(nvec, overall_power$Weibull, type = "o", lty = 2, pch = 2, col = "blue", lwd = 3)
lines(nvec, overall_power$Chi.Square, type = "o", lty = 3, pch = 8, col = "green", lwd = 3)
lines(nvec, overall_power$LogNormal, type = "o", lty = 4, pch = 4, col = "orange", lwd = 3)
lines(nvec, overall_power$Gamma, type = "o", lty = 5, pch = 5, col = "purple", lwd = 3)
lines(nvec, overall_power$Pareto, type = "o", lty = 5, pch = 6, col = "grey", lwd = 3)
title(main = "overall power of test")
legend("bottomright", legend=c("Exp", "Weibull", "Chisq", "LogNormal", "Gamma", "Pareto"), lwd = 3,
       col=c("red", "blue", "green", "orange", "purple", "grey"), lty = 1:6, pch =c(1,2,8, 4,5, 6), cex = 0.8, title = "Distribution")

plot(nvec, overall_power$Laplace, type = "o", lty = 1, pch = 1, col = "red", lwd = 3, 
     ylim = c(-0, 1), xlim = range(nvec), xlab = "Sample Size", ylab = "overall power of test")
lines(nvec, overall_power$Standard.Normal, type = "o", lty = 2, pch = 2, col = "blue", lwd = 3)
lines(nvec, overall_power$t, type = "o", lty = 3, pch = 8, col = "green", lwd = 3)
lines(nvec, overall_power$Contaminated, type = "o", lty = 5, pch = 6, col = "grey", lwd = 3)
lines(nvec, overall_power$Uniform, type = "o", lty = 5, pch = 4, col = "purple", lwd = 3)
title(main = "overall power of test")
legend("topleft", legend=c("Laplace", "Normal", "t", "Contaminated", "Uniform"), lwd = 3,
       col=c( "red", "blue", "green", "grey", "purple"), lty = 1:5,cex = 0.8, pch = c(1,2,8, 6, 4), title = "Distribution")
```




### Inflation of Type I error rate and Expected Inflation of Type I error rate


```{r}
rm(list = ls())
load("/Users/benedictkongyir/Desktop/OSU/Research/Pretest-Simulation/Simulation/EXPECTED POWER LOSS/TWO SAMPLE/TWO SAMPLES EXPECTED INFLATION OF TYPE I ERROR.RData")
#Probability of SW test
nvec = nvec[-1]
data_prob_SW <-data.frame(prob.non.sig.SW.test_par)[-1,]
# power loss
data_error <-data.frame(inflation_error)[-1,]
#Expected powerloss
Expected_inflation_error<-data_error * data_prob_SW
```

```{r}
#par(mar = c(9, 4, 4, 1), xpd = TRUE)
par(mfrow = c(2,2))
# Adjust margins to reduce space between plots
par(mai = c(0.75, 0.75, 0.2, 0.2))  # Adjust as needed
plot(nvec, data_error$Exponential,  type = "o", lty = 1, pch = 1, col = "red", lwd = 3, 
     ylim = c(-0.01, 0.3), xlim = range(nvec), xlab = "Sample Size", ylab = "Inflation of Type I error")
lines(nvec, data_error$Weibull, type = "o", lty = 2, pch = 2, col = "blue", lwd = 3)
lines(nvec, data_error$Chi.Square, type = "o", lty = 3, pch = 8, col = "green", lwd = 3)
lines(nvec, data_error$LogNormal, type = "o", lty = 4, pch = 4, col = "orange", lwd = 3)
lines(nvec, data_error$Gamma, type = "o", lty = 5, pch = 5, col = "purple", lwd = 3)
abline(h = 0, lwd = 2, col = "black", xpd = F)
title(main = "Inflation of Type I error")
legend("topleft", legend=c("Exp", "Weibull", "Chisq", "LogNormal", "Gamma"), lwd = 3,
       col=c("red", "blue", "green", "orange", "purple"), lty = 1:5, pch =c(1,2,8, 4, 5), cex = 0.8, title = "Distribution")

plot(nvec, data_error$Laplace, type = "o", lty = 1, pch = 1, col = "red", lwd = 3, 
     ylim = c(-0.01, 0.03), xlim = range(nvec), xlab = "Sample Size", ylab = "Inflation of Type I error rate")
lines(nvec, data_error$Standard.Normal, type = "o", lty = 2, pch = 2, col = "blue", lwd = 3)
lines(nvec, data_error$t, type = "o", lty = 3, pch = 8, col = "green", lwd = 3)
lines(nvec, data_error$Contaminated, type = "o", lty = 6, pch = 4, col = "brown", lwd = 3)
abline(h = 0, lwd = 2, col = "black", xpd = F)
title(main = "Inflation of Type I error")
legend("topleft", legend=c("Laplace", "Normal", "t", "Contaminated"), lwd = 3,
       col=c( "red", "blue", "green", "brown"), lty = 1:4, pch = c(1, 2, 8, 4), cex = 0.8, title = "Distribution")

### Expected power loss
plot(nvec, Expected_inflation_error$Exponential,  type = "o", lty = 1, pch = 1, col = "red", lwd = 3, 
     ylim = c(-0.01, 0.03), xlim = range(nvec), xlab = "Sample Size", ylab = "Expected Inflation of Type I error")
lines(nvec, Expected_inflation_error$Weibull, type = "o", lty = 2, pch = 2, col = "blue", lwd = 3)
lines(nvec, Expected_inflation_error$Chi.Square, type = "o", lty = 3, pch = 8, col = "green", lwd = 3)
lines(nvec, Expected_inflation_error$LogNormal, type = "o", lty = 4, pch = 4, col = "orange", lwd = 3)
lines(nvec, Expected_inflation_error$Gamma, type = "o", lty = 5, pch = 5, col = "purple", lwd = 3)
abline(h = 0, lwd = 2, col = "black", xpd = F)
title(main = "Expected Inflation of Type I error")
legend("topleft", legend=c("Exp", "Weibull", "Chisq", "LogNormal", "Gamma"), lwd = 3,
       col=c("red", "blue", "green", "orange", "purple"), lty = 1:5, pch =c(1,2,8, 4,5), cex = 0.8, title = "Distribution")

plot(nvec, Expected_inflation_error$Laplace, type = "o", lty = 1, pch = 1, col = "red", lwd = 3, 
     ylim = c(-0.01, 0.03), xlim = range(nvec), xlab = "Sample Size", ylab = "Expected Inflation of Type I error")
lines(nvec, Expected_inflation_error$Standard.Normal, type = "o", lty = 2, pch = 2, col = "blue", lwd = 3)
lines(nvec, Expected_inflation_error$t, type = "o", lty = 3, pch = 8, col = "green", lwd = 3)
lines(nvec, data_error$Contaminated, type = "o", lty = 6, pch = 4, col = "brown", lwd = 3)
abline(h = 0, lwd = 2, col = "black", xpd = F)
title(main = "Expected Inflation of Type I error")
legend("topleft", legend=c("Laplace", "Normal", "t", "Contaminated"), lwd = 3,
       col=c( "red", "blue", "green", "brown"), lty = 1:3, pch = c(1, 2, 8, 4), cex = 0.8, title = "Distribution")
```


### Type I error rate of Two sample two-stage procedure

### Observations:
Type I error rate is inflated for samples drawn from skewed distributions under t test and for symmetric distributions under the U test. 
Type I error rate is controlled under t for symmetric distributions, likewise under U for skewed distributions.

Type I error rates are controlled for both skewed and symmetric distributions for the two-stage procedure.

```{r}
rm(list = ls())
load("/Users/benedictkongyir/Desktop/OSU/Research/Pretest-Simulation/Simulation/EXPECTED POWER LOSS/TWO SAMPLE/TWOSAMPLE.TYPEI.ERROR.TWOSTAGE.PROCEDURE.RData")
#Probability of SW test
TypeI.error.t.test <-data.frame(TypeI.error.t.test)
# power loss
TypeI.error.U.test <-data.frame(TypeI.error.U.test)
#Expected powerloss
overall_TypeI.error<-data.frame(overall_TypeI.error)
```

```{r , fig.height=10, fig.width=10}
#par(mar = c(9, 4, 4, 1), xpd = TRUE)
par(mfrow = c(3,2))
# Adjust margins to reduce space between plots
par(mai = c(0.75, 0.75, 0.2, 0.2))  # Adjust as needed
### Type I error rate of t test
plot(nvec, TypeI.error.t.test$Exponential,  type = "o", lty = 1, pch = 1, col = "red", lwd = 3, 
     ylim = c(0.02, 0.4), xlim = range(nvec), xlab = "Sample Size", ylab = "Type I error")
lines(nvec, TypeI.error.t.test$Weibull, type = "o", lty = 2, pch = 2, col = "blue", lwd = 3)
lines(nvec, TypeI.error.t.test$Chi.Square, type = "o", lty = 3, pch = 8, col = "green", lwd = 3)
lines(nvec, TypeI.error.t.test$LogNormal, type = "o", lty = 4, pch = 4, col = "orange", lwd = 3)
lines(nvec, TypeI.error.t.test$Gamma, type = "o", lty = 5, pch = 5, col = "purple", lwd = 3)
abline(h = 0.05, lwd = 2, col = "black", xpd = F)
title(main = "Type I error of t test")
legend("topleft", legend=c("Exp", "Weibull", "Chisq", "LogNormal", "Gamma"), lwd = 3,
       col=c("red", "blue", "green", "orange", "purple"), lty = 1:5, pch =c(1,2,8, 4, 5), cex = 0.8, title = "Distribution")

plot(nvec, TypeI.error.t.test$Laplace, type = "o", lty = 1, pch = 1, col = "red", lwd = 3, 
     ylim = c(0.02, 0.08), xlim = range(nvec), xlab = "Sample Size", ylab = "Type I error rate")
lines(nvec, TypeI.error.t.test$Standard.Normal, type = "o", lty = 2, pch = 2, col = "blue", lwd = 3)
lines(nvec, TypeI.error.t.test$t, type = "o", lty = 3, pch = 8, col = "green", lwd = 3)
lines(nvec, TypeI.error.t.test$Contaminated, type = "o", lty = 6, pch = 4, col = "brown", lwd = 3)
abline(h = 0.05, lwd = 2, col = "black", xpd = F)
title(main = "Type I error of t test")
legend("topleft", legend=c("Laplace", "Normal", "t", "Contaminated"), lwd = 3,
       col=c( "red", "blue", "green", "brown"), lty = 1:4, pch = c(1, 2, 8, 4), cex = 0.8, title = "Distribution")

### Type I error rate of Mann-Whitney U test
plot(nvec, TypeI.error.U.test$Exponential,  type = "o", lty = 1, pch = 1, col = "red", lwd = 3, 
     ylim = c(0.02, 0.08), xlim = range(nvec), xlab = "Sample Size", ylab = "Expected Inflation of Type I error")
lines(nvec, TypeI.error.U.test$Weibull, type = "o", lty = 2, pch = 2, col = "blue", lwd = 3)
lines(nvec, TypeI.error.U.test$Chi.Square, type = "o", lty = 3, pch = 8, col = "green", lwd = 3)
lines(nvec, TypeI.error.U.test$LogNormal, type = "o", lty = 4, pch = 4, col = "orange", lwd = 3)
lines(nvec, TypeI.error.U.test$Gamma, type = "o", lty = 5, pch = 5, col = "purple", lwd = 3)
abline(h = 0.05, lwd = 2, col = "black", xpd = F)
title(main = "Type I error of Mann-Whitney test")
legend("topleft", legend=c("Exp", "Weibull", "Chisq", "LogNormal", "Gamma"), lwd = 3,
       col=c("red", "blue", "green", "orange", "purple"), lty = 1:5, pch =c(1,2,8, 4,5), cex = 0.8, title = "Distribution")

plot(nvec, TypeI.error.U.test$Laplace, type = "o", lty = 1, pch = 1, col = "red", lwd = 3, 
     ylim = c(0.02, 0.08), xlim = range(nvec), xlab = "Sample Size", ylab = "Type I error")
lines(nvec, TypeI.error.U.test$Standard.Normal, type = "o", lty = 2, pch = 2, col = "blue", lwd = 3)
lines(nvec, TypeI.error.U.test$t, type = "o", lty = 3, pch = 8, col = "green", lwd = 3)
lines(nvec, TypeI.error.U.test$Contaminated, type = "o", lty = 6, pch = 4, col = "brown", lwd = 3)
abline(h = 0.05, lwd = 2, col = "black", xpd = F)
title(main = "Type I error Mann-Whitney test")
legend("topleft", legend=c("Laplace", "Normal", "t", "Contaminated"), lwd = 3,
       col=c( "red", "blue", "green", "brown"), lty = 1:3, pch = c(1, 2, 8, 4), cex = 0.8, title = "Distribution")

## ### Type I error rate of two-stage procedure
plot(nvec, overall_TypeI.error$Exponential,  type = "o", lty = 1, pch = 1, col = "red", lwd = 3, 
     ylim = c(0.02, 0.08), xlim = range(nvec), xlab = "Sample Size", ylab = "EType I error")
lines(nvec, overall_TypeI.error$Weibull, type = "o", lty = 2, pch = 2, col = "blue", lwd = 3)
lines(nvec, overall_TypeI.error$Chi.Square, type = "o", lty = 3, pch = 8, col = "green", lwd = 3)
lines(nvec, overall_TypeI.error$LogNormal, type = "o", lty = 4, pch = 4, col = "orange", lwd = 3)
lines(nvec, overall_TypeI.error$Gamma, type = "o", lty = 5, pch = 5, col = "purple", lwd = 3)
abline(h = 0.05, lwd = 2, col = "black", xpd = F)
title(main = "Overall Type I error rate of two-stage procedure")
legend("topleft", legend=c("Exp", "Weibull", "Chisq", "LogNormal", "Gamma"), lwd = 3,
       col=c("red", "blue", "green", "orange", "purple"), lty = 1:5, pch =c(1,2,8, 4,5), cex = 0.8, title = "Distribution")

plot(nvec, overall_TypeI.error$Laplace, type = "o", lty = 1, pch = 1, col = "red", lwd = 3, 
     ylim = c(0.02, 0.08), xlim = range(nvec), xlab = "Sample Size", ylab = "Type I error")
lines(nvec, overall_TypeI.error$Standard.Normal, type = "o", lty = 2, pch = 2, col = "blue", lwd = 3)
lines(nvec, overall_TypeI.error$t, type = "o", lty = 3, pch = 8, col = "green", lwd = 3)
lines(nvec, overall_TypeI.error$Contaminated, type = "o", lty = 6, pch = 4, col = "brown", lwd = 3)
abline(h = 0.05, lwd = 2, col = "black", xpd = F)
title(main = "Overall Type I error rate of two-stage procedure")
legend("topleft", legend=c("Laplace", "Normal", "t", "Contaminated"), lwd = 3,
       col=c( "red", "blue", "green", "brown"), lty = 1:3, pch = c(1, 2, 8, 4), cex = 0.8, title = "Distribution")
```

