---
title: "Utility of Normality test in Two Samples test"
author: "Benedict Kongyir"
date: "`r format(Sys.time(), '%m/%d/%Y')`"
output: 
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.height = 6.5, fig.width = 8)
```


```{r}
rm(list = ls())
#setwd("/Users/benedictkongyir/Desktop/OSU/Research/Permutation Test/New Simulations/cluster/Results")
load("/Users/benedictkongyir/Desktop/OSU/Research/Permutation Test/New Simulations/cluster/Parrel_sim_RData/TwoSamples_power_norm_par.RData")
load("/Users/benedictkongyir/Desktop/OSU/Research/Permutation Test/New Simulations/cluster/Parrel_sim_RData/TwoSamples_powerloss_par.RData")
```



```{r}
data_powertest <-data.frame(power_norm.test_par)[-1,]
data_powerloss <-data.frame(power_loss_par)
#data.combine <- data.frame(data_powertest, data_powerloss)
#nvec = nvec[-1]
#data_powerloss = data_powerloss[-1,]
```

 

### Type I error for Different Normality Tests

```{r}
par(mar = c(5.0, 4.0, 4.0, 6.5), xpd = TRUE)
plot(nvec, data_powertest$Standard.Normal.KS, type="l", lwd= 2, col = "red", 
     ylim = c(0.0, 0.1),xlab = "Sample Size", ylab = "Type I error")
lines(nvec, data_powertest$Standard.Normal.SW, lwd= 2, col = "blue")
lines(nvec, data_powertest$Standard.Normal.JB,lwd= 2, col = "gold")
lines(nvec, data_powertest$Standard.Normal.DAP,lwd= 2, col = "green")
lines(nvec, data_powertest$Standard.Normal.AD, col = "coral4")
lines(nvec, data_powertest$Standard.Normal.SF, col = "deeppink")
title(main = "Normal Distribution")
legend("topright", inset = c(-0.2, 0), legend=c("KS", "SW", "JB", "DAP", "AD", "SF"),
       col=c( "red","blue", "gold", "green", "coral4", "deeppink"), lty =1,cex = 0.8, title = "Test Method")
```



### Power Normality Tests for t

```{r}
par(mar = c(5.0, 4.0, 4.0, 6.5), xpd = TRUE)
plot(nvec, data_powertest$t.KS, type="l", lwd= 2, col = "red", 
     ylim = c(0.0, 1.0),xlab = "Sample Size", ylab = "Power")
lines(nvec, data_powertest$t.SW, lwd= 2, col = "blue")
lines(nvec, data_powertest$t.JB,lwd= 2, col = "gold")
lines(nvec, data_powertest$t.DAP,lwd= 2, col = "green")
lines(nvec, data_powertest$t.AD, col = "coral4")
lines(nvec, data_powertest$t.SF, col = "deeppink")
title(main = "t Distribution")
legend("topright", inset = c(-0.2, 0), legend=c("KS", "SW", "JB", "DAP", "AD", "SF"),
       col=c( "red","blue", "gold", "green", "coral4", "deeppink"), lty =1,cex = 0.8, title = "Test Method")
```


### Power of Normality Tests for Uniform

```{r}
par(mar = c(5.0, 4.0, 4.0, 6.5), xpd = TRUE)
plot(nvec, data_powertest$Uniform.KS, type="l", lwd= 2, col = "red", 
     ylim = c(0.0, 1.0),xlab = "Sample Size", ylab = "Power")
lines(nvec, data_powertest$Uniform.SW, lwd= 2, col = "blue")
lines(nvec, data_powertest$Uniform.JB,lwd= 2, col = "gold")
lines(nvec, data_powertest$Uniform.DAP,lwd= 2, col = "green")
lines(nvec, data_powertest$Uniform.AD, col = "coral4")
lines(nvec, data_powertest$Uniform.SF, col = "deeppink")
title(main = "Uniform Distribution")
legend("topright", inset = c(-0.2, 0), legend=c("KS", "SW", "JB", "DAP", "AD", "SF"),
       col=c( "red","blue", "gold", "green", "coral4", "deeppink"), lty =1,cex = 0.8, title = "Test Method")
```

### Power of Different Normality Tests for Contaminated
```{r}
par(mar = c(5.0, 4.0, 4.0, 6.5), xpd = TRUE)
plot(nvec, data_powertest$Contaminated.KS, type="l", lwd= 2, col = "red", 
     ylim = c(0.0, 1.0),xlab = "Sample Size", ylab = "Power")
lines(nvec, data_powertest$Contaminated.SW, lwd= 2, col = "blue")
lines(nvec, data_powertest$Contaminated.JB,lwd= 2, col = "gold")
lines(nvec, data_powertest$Contaminated.DAP,lwd= 2, col = "green")
lines(nvec, data_powertest$Contaminated.AD, col = "coral4")
lines(nvec, data_powertest$Contaminated.SF, col = "deeppink")
title(main = "Contaminated Distribution")
legend("topright", inset = c(-0.2, 0), legend=c("KS", "SW", "JB", "DAP", "AD", "SF"),
       col=c( "red","blue", "gold", "green", "coral4", "deeppink"), lty =1,cex = 0.8, title = "Test Method")
```


### Power of Different Normality Tests for Laplace
```{r}
par(mar = c(5.0, 4.0, 4.0, 6.5), xpd = TRUE)
plot(nvec, data_powertest$Laplace.KS, type="l", lwd= 2, col = "red", 
     ylim = c(0.0, 1.0),xlab = "Sample Size", ylab = "Power")
lines(nvec, data_powertest$Laplace.SW, lwd= 2, col = "blue")
lines(nvec, data_powertest$Laplace.JB,lwd= 2, col = "gold")
lines(nvec, data_powertest$Laplace.DAP,lwd= 2, col = "green")
lines(nvec, data_powertest$Laplace.AD, col = "coral4")
lines(nvec, data_powertest$Laplace.SF, col = "deeppink")
title(main = "Laplace Distribution")
legend("topright", inset = c(-0.2, 0), legend=c("KS", "SW", "JB", "DAP", "AD", "SF"),
       col=c( "red","blue", "gold", "green", "coral4", "deeppink"), lty =1,cex = 0.8, title = "Test Method")
```


### Power of Different Normality Tests for Chi-Square
```{r}
par(mar = c(5.0, 4.0, 4.0, 6.5), xpd = TRUE)
plot(nvec, data_powertest$Chi.Square.KS, type="l", lwd= 2, col = "red", 
     ylim = c(0.0, 1.0),xlab = "Sample Size", ylab = "Power")
lines(nvec, data_powertest$Chi.Square.SW, lwd= 2, col = "blue")
lines(nvec, data_powertest$Chi.Square.JB,lwd= 2, col = "gold")
lines(nvec, data_powertest$Chi.Square.DAP,lwd= 2, col = "green")
lines(nvec, data_powertest$Chi.Square.AD, col = "coral4")
lines(nvec, data_powertest$Chi.Square.SF, col = "deeppink")
title(main = "Chi-Square Distribution")
legend("topright", inset = c(-0.2, 0), legend=c("KS", "SW", "JB", "DAP", "AD", "SF"),
       col=c( "red","blue", "gold", "green", "coral4", "deeppink"), lty =1,cex = 0.8, title = "Test Method")
```


### Power of Different Normality Tests for Gamma
```{r}
par(mar = c(5.0, 4.0, 4.0, 6.5), xpd = TRUE)
plot(nvec, data_powertest$Gamma.KS, type="l", lwd= 2, col = "red", 
     ylim = c(0.0, 1.0),xlab = "Sample Size", ylab = "Power")
lines(nvec, data_powertest$Gamma.SW, lwd= 2, col = "blue")
lines(nvec, data_powertest$Gamma.JB,lwd= 2, col = "gold")
lines(nvec, data_powertest$Gamma.DAP,lwd= 2, col = "green")
lines(nvec, data_powertest$Gamma.AD, col = "coral4")
lines(nvec, data_powertest$Gamma.SF, col = "deeppink")
title(main = "Gamma Distribution")
legend("topright", inset = c(-0.2, 0), legend=c("KS", "SW", "JB", "DAP", "AD", "SF"),
       col=c( "red","blue", "gold", "green", "coral4", "deeppink"), lty =1,cex = 0.8, title = "Test Method")
```


### Power of Different Normality Tests for Exponential 
```{r}
par(mar = c(5.0, 4.0, 4.0, 6.5), xpd = TRUE)
plot(nvec, data_powertest$Exponential.KS, type="l", lwd= 2, col = "red", 
     ylim = c(0.0, 1.0),xlab = "Sample Size", ylab = "Power")
lines(nvec, data_powertest$Exponential.SW, lwd= 2, col = "blue")
lines(nvec, data_powertest$Exponential.JB,lwd= 2, col = "gold")
lines(nvec, data_powertest$Exponential.DAP,lwd= 2, col = "green")
lines(nvec, data_powertest$Exponential.AD, col = "coral4")
lines(nvec, data_powertest$Exponential.SF, col = "deeppink")
title(main = "Exponential Distribution")
legend("topright", inset = c(-0.2, 0), legend=c("KS", "SW", "JB", "DAP", "AD", "SF"),
       col=c( "red","blue", "gold", "green", "coral4", "deeppink"), lty =1,cex = 0.8, title = "Test Method")
```



### Power of Different Normality Tests for Weibull
```{r}
par(mar = c(5.0, 4.0, 4.0, 6.5), xpd = TRUE)
plot(nvec, data_powertest$Weibull.KS, type="l", lwd= 2, col = "red", 
     ylim = c(0.0, 1.0),xlab = "Sample Size", ylab = "Power")
lines(nvec, data_powertest$Weibull.SW, lwd= 2, col = "blue")
lines(nvec, data_powertest$Weibull.JB,lwd= 2, col = "gold")
lines(nvec, data_powertest$Weibull.DAP,lwd= 2, col = "green")
lines(nvec, data_powertest$Weibull.AD, col = "coral4")
lines(nvec, data_powertest$Weibull.SF, col = "deeppink")
title(main = "Weibull Distribution")
legend("topright", inset = c(-0.2, 0), legend=c("KS", "SW", "JB", "DAP", "AD", "SF"),
       col=c( "red","blue", "gold", "green", "coral4", "deeppink"), lty =1,cex = 0.8, title = "Test Method")
```



### Power of Different Normality Tests for LogNormal
```{r}
par(mar = c(5.0, 4.0, 4.0, 6.5), xpd = TRUE)
plot(nvec, data_powertest$LogNormal.KS, type="l", lwd= 2, col = "red", 
     ylim = c(0.0, 1.0),xlab = "Sample Size", ylab = "Power")
lines(nvec, data_powertest$LogNormal.SW, lwd= 2, col = "blue")
lines(nvec, data_powertest$LogNormal.JB,lwd= 2, col = "gold")
lines(nvec, data_powertest$LogNormal.DAP,lwd= 2, col = "green")
lines(nvec, data_powertest$LogNormal.AD, col = "coral4")
lines(nvec, data_powertest$LogNormal.SF, col = "deeppink")
title(main = "LogNormal Distribution")
legend("topright", inset = c(-0.2, 0), legend=c("KS", "SW", "JB", "DAP", "AD", "SF"),
       col=c( "red","blue", "gold", "green", "coral4", "deeppink"), lty =1,cex = 0.8, title = "Test Method")
```


### Genereal Comments

#### Symmetric distributions

The power to detect departures from normality is less for all the different normality test methods for samples coming from symmetric distribution like the uniform, t, Laplace and contaminated distributions as shown in the plots above especially for smaller sample sizes. Jaque-Bera, Shapiro-Wilk, Shapiro-Francia test and the Aderson-Darling test are the best test for samples from t, uniform, Laplace and contaminated distributions receptively. This shows the deficiency in the various existing normality methods to detect departures from normality for samples coming from the symmetric distribution especially for smaller sample sizes.

#### Asymmetric distributions

For Asymmetry distributions such as Chi-Square, Exponential, Gamma, Weibull, and LogNormal distributions, the power to detect departures from normality is generally high with the Shapiro-Wilk test method being the best for all distributions.
The above observations further emphasize the luck of a single best test method under all scenarios.


### Utility of SW test---Exponential Distributions
```{r}
## add extra space to right margin of plot within frame
par(mar = c(9, 4.1, 3.1, 6.5), xpd = TRUE)
plot(nvec, data_powertest$Exponential.SW, axes=FALSE, ylim=c(0,1), xlab="", ylab="", 
   type="o", lwd = 2, col="black", main="Utility of SW test ... Exponential Samples")
axis(2, ylim=c(0,1),col="black",las=1)  
mtext("Power of SW test",side=2,line=2.5)
box()
par(new=TRUE)

## Plot the second plot and put axis scale on right
plot(nvec, data_powerloss$Exponential.0.5,  xlab="", ylab="", ylim=c(-0.01,0.1), 
    axes=FALSE, type="l", lty = 2, lwd = 2, col="red")
mtext("Power loss of t test",side=4,col="black",line=4) 
axis(4, ylim=c(0,0.5), col="red",col.axis="black",las=1)
## a little farther out (line=4) to make room for labels
axis(4, ylim=c(0,0.2), col="blue",col.axis="blue",las=1)

## Draw the time axis
axis(1,pretty(range(nvec),10))
mtext("Sample Size",side=1,col="black",line=2.5)  
## Add Legend
legend("bottom", inset = c(0, -0.3), legend=c("power of SW test","powerloss of t test"),
  col=c("black","red"), lty = c(1, 2), horiz = TRUE)

```


### Utility of SW test---LogNormal Distributions
```{r}

## add extra space to right margin of plot within frame
par(mar = c(9, 4.1, 3.1, 6.5), xpd = TRUE)
plot(nvec, data_powertest$LogNormal.SW, axes=FALSE, ylim=c(0,1), xlab="", ylab="", 
   type="o", lwd = 2, col="black", main="Utility of SW test ... LogNormal Samples")
axis(2, ylim=c(0,1),col="black",las=1)  
mtext("Power of SW test",side=2,line=2.5)
box()
par(new=TRUE)

## Plot the second plot and put axis scale on right
plot(nvec, data_powerloss$LogNormal.0.5,  xlab="", ylab="", ylim=c(-0.01,0.1), 
    axes=FALSE, type="l", lty = 2, lwd = 2, col="red")
mtext("Power loss of t test",side=4,col="black",line=4) 
axis(4, ylim=c(0,0.5), col="red",col.axis="black",las=1)
## a little farther out (line=4) to make room for labels
axis(4, ylim=c(0,0.2), col="blue",col.axis="blue",las=1)

## Draw the time axis
axis(1,pretty(range(nvec),10))
mtext("Sample Size",side=1,col="black",line=2.5)  
## Add Legend
legend("bottom", inset = c(0, -0.3), legend=c("power of SW test","powerloss of t test"),
  col=c("black","red"), lty = c(1, 2), horiz = TRUE)
```


### Utility of SW test---Chi-Square Distributions
```{r}

## add extra space to right margin of plot within frame
par(mar = c(9, 4.1, 3.1, 6.5), xpd = TRUE)
plot(nvec, data_powertest$Chi.Square.SW, axes=FALSE, ylim=c(0,1), xlab="", ylab="", 
   type="o", lwd = 2, col="black", main="Utility of SW test ... Chi-Square Samples")
axis(2, ylim=c(0,1),col="black",las=1)  
mtext("Power of SW test",side=2,line=2.5)
box()
par(new=TRUE)

## Plot the second plot and put axis scale on right
plot(nvec, data_powerloss$Chi.Square.0.5,  xlab="", ylab="", ylim=c(-0.01,0.1), 
    axes=FALSE, type="l", lty = 2, lwd = 2, col="red")
mtext("Power loss of t test",side=4,col="black",line=4) 
axis(4, ylim=c(0,0.5), col="red",col.axis="black",las=1)
## a little farther out (line=4) to make room for labels
axis(4, ylim=c(0,0.2), col="blue",col.axis="blue",las=1)

## Draw the time axis
axis(1,pretty(range(nvec),10))
mtext("Sample Size",side=1,col="black",line=2.5)  
## Add Legend
legend("bottom", inset = c(0, -0.3), legend=c("power of SW test","powerloss of t test"),
  col=c("black","red"), lty = c(1, 2), horiz = TRUE)
```



### Utility of SW test---Weibull Distributions
```{r}

## add extra space to right margin of plot within frame
par(mar = c(9, 4.1, 3.1, 6.5), xpd = TRUE)
plot(nvec, data_powertest$Weibull.SW, axes=FALSE, ylim=c(0,1), xlab="", ylab="", 
   type="o", lwd = 2, col="black", main="Utility of SW test ... Weibull Samples")
axis(2, ylim=c(0,1),col="black",las=1)  
mtext("Power of SW test",side=2,line=2.5)
box()
par(new=TRUE)

## Plot the second plot and put axis scale on right
plot(nvec, data_powerloss$Weibull.0.5,  xlab="", ylab="", ylim=c(-0.01,0.1), 
    axes=FALSE, type="l", lty = 2, lwd = 2, col="red")
mtext("Power loss of t test",side=4,col="black",line=4) 
axis(4, ylim=c(0,0.5), col="red",col.axis="black",las=1)
## a little farther out (line=4) to make room for labels
axis(4, ylim=c(0,0.2), col="blue",col.axis="blue",las=1)

## Draw the time axis
axis(1,pretty(range(nvec),10))
mtext("Sample Size",side=1,col="black",line=2.5)  
## Add Legend
legend("bottom", inset = c(0, -0.3), legend=c("power of SW test","powerloss of t test"),
  col=c("black","red"), lty = c(1, 2), horiz = TRUE)
```




### Utility of SW test---Gamma Distributions
```{r}

## add extra space to right margin of plot within frame
par(mar = c(9, 4.1, 3.1, 6.5), xpd = TRUE)
plot(nvec, data_powertest$Gamma.SW, axes=FALSE, ylim=c(0,1), xlab="", ylab="", 
   type="o", lwd = 2, col="black", main="Utility of SW test ... LogNormal Samples")
axis(2, ylim=c(0,1),col="black",las=1)  
mtext("Power of SW test",side=2,line=2.5)
box()
par(new=TRUE)

## Plot the second plot and put axis scale on right
plot(nvec, data_powerloss$Gamma.0.5,  xlab="", ylab="", ylim=c(-0.01,0.1), 
    axes=FALSE, type="l", lty = 2, lwd = 2, col="red")
mtext("Power loss of t test",side=4,col="black",line=4) 
axis(4, ylim=c(0,0.5), col="red",col.axis="black",las=1)
## a little farther out (line=4) to make room for labels
axis(4, ylim=c(0,0.2), col="blue",col.axis="blue",las=1)

## Draw the time axis
axis(1,pretty(range(nvec),10))
mtext("Sample Size",side=1,col="black",line=2.5)  
## Add Legend
legend("bottom", inset = c(0, -0.3), legend=c("power of SW test","powerloss of t test"),
  col=c("black","red"), lty = c(1, 2), horiz = TRUE)
```



### Utility of SW test---Normal Distributions
```{r}

## add extra space to right margin of plot within frame
par(mar = c(9, 4.1, 3.1, 6.5), xpd = TRUE)
plot(nvec, data_powertest$Standard.Normal.SW, axes=FALSE, ylim=c(0,1), xlab="", ylab="", 
   type="o", lwd = 2, col="black", main="Utility of SW test ... Normal Samples")
axis(2, ylim=c(0,1),col="black",las=1)  
mtext("Power of SW test",side=2,line=2.5)
box()
par(new=TRUE)

## Plot the second plot and put axis scale on right
plot(nvec, data_powerloss$Standard.Normal.0.5,  xlab="", ylab="", ylim=c(-0.01,0.1), 
    axes=FALSE, type="l", lty = 2, lwd = 2, col="red")
mtext("Power loss of t test",side=4,col="black",line=4) 
axis(4, ylim=c(0,0.5), col="red",col.axis="black",las=1)
## a little farther out (line=4) to make room for labels
axis(4, ylim=c(0,0.2), col="blue",col.axis="blue",las=1)

## Draw the time axis
axis(1,pretty(range(nvec),10))
mtext("Sample Size",side=1,col="black",line=2.5)  
## Add Legend
legend("bottom", inset = c(0, -0.3), legend=c("power of SW test","powerloss of t test"),
  col=c("black","red"), lty = c(1, 2), horiz = TRUE)
```



### Utility of SW test---t Distributions
```{r}

## add extra space to right margin of plot within frame
par(mar = c(9, 4.1, 3.1, 6.5), xpd = TRUE)
plot(nvec, data_powertest$t.SW, axes=FALSE, ylim=c(0,1), xlab="", ylab="", 
   type="o", lwd = 2, col="black", main="Utility of SW test ... t Samples")
axis(2, ylim=c(0,1),col="black",las=1)  
mtext("Power of SW test",side=2,line=2.5)
box()
par(new=TRUE)

## Plot the second plot and put axis scale on right
plot(nvec, data_powerloss$t.0.5,  xlab="", ylab="", ylim=c(-0.01,0.1), 
    axes=FALSE, type="l", lty = 2, lwd = 2, col="red")
mtext("Power loss of t test",side=4,col="black",line=4) 
axis(4, ylim=c(0,0.5), col="red",col.axis="black",las=1)
## a little farther out (line=4) to make room for labels
axis(4, ylim=c(0,0.2), col="blue",col.axis="blue",las=1)

## Draw the time axis
axis(1,pretty(range(nvec),10))
mtext("Sample Size",side=1,col="black",line=2.5)  
## Add Legend
legend("bottom", inset = c(0, -0.3), legend=c("power of SW test","powerloss of t test"),
  col=c("black","red"), lty = c(1, 2), horiz = TRUE)
```


### Utility of SW test---Uniform Distributions
```{r}

## add extra space to right margin of plot within frame
par(mar = c(9, 4.1, 3.1, 6.5), xpd = TRUE)
plot(nvec, data_powertest$Uniform.SW, axes=FALSE, ylim=c(0,1), xlab="", ylab="", 
   type="o", lwd = 2, col="black", main="Utility of SW test ... Uniform Samples")
axis(2, ylim=c(0,1),col="black",las=1)  
mtext("Power of SW test",side=2,line=2.5)
box()
par(new=TRUE)

## Plot the second plot and put axis scale on right
plot(nvec, data_powerloss$Uniform.0.5,  xlab="", ylab="", ylim=c(-0.01,0.1), 
    axes=FALSE, type="l", lty = 2, lwd = 2, col="red")
mtext("Power loss of t test",side=4,col="black",line=4) 
axis(4, ylim=c(0,0.5), col="red",col.axis="black",las=1)
## a little farther out (line=4) to make room for labels
axis(4, ylim=c(0,0.2), col="blue",col.axis="blue",las=1)

## Draw the time axis
axis(1,pretty(range(nvec),10))
mtext("Sample Size",side=1,col="black",line=2.5)  
## Add Legend
legend("bottom", inset = c(0, -0.3), legend=c("power of SW test","powerloss of t test"),
  col=c("black","red"), lty = c(1, 2), horiz = TRUE)
```


### Utility of KS test---Exponential Distributions
```{r}
## add extra space to right margin of plot within frame
par(mar = c(9, 4.1, 3.1, 6.5), xpd = TRUE)
plot(nvec, data_powertest$Exponential.KS, axes=FALSE, ylim=c(0,1), xlab="", ylab="", 
   type="o", lwd = 2, col="black", main="Utility of SW test ... Exponential Samples")
axis(2, ylim=c(0,1),col="black",las=1)  
mtext("Power of SW test",side=2,line=2.5)
box()
par(new=TRUE)

## Plot the second plot and put axis scale on right
plot(nvec, data_powerloss$Exponential.0.5,  xlab="", ylab="", ylim=c(-0.01,0.1), 
    axes=FALSE, type="l", lty = 2, lwd = 2, col="red")
mtext("Power loss of t test",side=4,col="black",line=4) 
axis(4, ylim=c(0,0.5), col="red",col.axis="black",las=1)
## a little farther out (line=4) to make room for labels
axis(4, ylim=c(0,0.2), col="blue",col.axis="blue",las=1)

## Draw the time axis
axis(1,pretty(range(nvec),10))
mtext("Sample Size",side=1,col="black",line=2.5)  
## Add Legend
legend("bottom", inset = c(0, -0.3), legend=c("power of KS test","powerloss of t test"),
  col=c("black","red"), lty = c(1, 2), horiz = TRUE)

```


### Utility of KS test---LogNormal Distributions
```{r}

## add extra space to right margin of plot within frame
par(mar = c(9, 4.1, 3.1, 6.5), xpd = TRUE)
plot(nvec, data_powertest$LogNormal.KS, axes=FALSE, ylim=c(0,1), xlab="", ylab="", 
   type="o", lwd = 2, col="black", main="Utility of KS test ... LogNormal Samples")
axis(2, ylim=c(0,1),col="black",las=1)  
mtext("Power of SW test",side=2,line=2.5)
box()
par(new=TRUE)

## Plot the second plot and put axis scale on right
plot(nvec, data_powerloss$LogNormal.0.5,  xlab="", ylab="", ylim=c(-0.01,0.1), 
    axes=FALSE, type="l", lty = 2, lwd = 2, col="red")
mtext("Power loss of t test",side=4,col="black",line=4) 
axis(4, ylim=c(0,0.5), col="red",col.axis="black",las=1)
## a little farther out (line=4) to make room for labels
axis(4, ylim=c(0,0.2), col="blue",col.axis="blue",las=1)

## Draw the time axis
axis(1,pretty(range(nvec),10))
mtext("Sample Size",side=1,col="black",line=2.5)  
## Add Legend
legend("bottom", inset = c(0, -0.3), legend=c("power of KS test","powerloss of t test"),
  col=c("black","red"), lty = c(1, 2), horiz = TRUE)
```


### Utility of KS test---Chi-Square Distributions
```{r}

## add extra space to right margin of plot within frame
par(mar = c(9, 4.1, 3.1, 6.5), xpd = TRUE)
plot(nvec, data_powertest$Chi.Square.KS, axes=FALSE, ylim=c(0,1), xlab="", ylab="", 
   type="o", lwd = 2, col="black", main="Utility of KS test ... Chi-Square Samples")
axis(2, ylim=c(0,1),col="black",las=1)  
mtext("Power of SW test",side=2,line=2.5)
box()
par(new=TRUE)

## Plot the second plot and put axis scale on right
plot(nvec, data_powerloss$Chi.Square.0.5,  xlab="", ylab="", ylim=c(-0.01,0.1), 
    axes=FALSE, type="l", lty = 2, lwd = 2, col="red")
mtext("Power loss of t test",side=4,col="black",line=4) 
axis(4, ylim=c(0,0.5), col="red",col.axis="black",las=1)
## a little farther out (line=4) to make room for labels
axis(4, ylim=c(0,0.2), col="blue",col.axis="blue",las=1)

## Draw the time axis
axis(1,pretty(range(nvec),10))
mtext("Sample Size",side=1,col="black",line=2.5)  
## Add Legend
legend("bottom", inset = c(0, -0.3), legend=c("power of KS test","powerloss of t test"),
  col=c("black","red"), lty = c(1, 2), horiz = TRUE)
```



### Utility of KS test---Weibull Distributions
```{r}

## add extra space to right margin of plot within frame
par(mar = c(9, 4.1, 3.1, 6.5), xpd = TRUE)
plot(nvec, data_powertest$Weibull.KS, axes=FALSE, ylim=c(0,1), xlab="", ylab="", 
   type="o", lwd = 2, col="black", main="Utility of SW test ... Weibull Samples")
axis(2, ylim=c(0,1),col="black",las=1)  
mtext("Power of KS test",side=2,line=2.5)
box()
par(new=TRUE)

## Plot the second plot and put axis scale on right
plot(nvec, data_powerloss$Weibull.0.5,  xlab="", ylab="", ylim=c(-0.01,0.1), 
    axes=FALSE, type="l", lty = 2, lwd = 2, col="red")
mtext("Power loss of t test",side=4,col="black",line=4) 
axis(4, ylim=c(0,0.5), col="red",col.axis="black",las=1)
## a little farther out (line=4) to make room for labels
axis(4, ylim=c(0,0.2), col="blue",col.axis="blue",las=1)

## Draw the time axis
axis(1,pretty(range(nvec),10))
mtext("Sample Size",side=1,col="black",line=2.5)  
## Add Legend
legend("bottom", inset = c(0, -0.3), legend=c("power of KS test","powerloss of t test"),
  col=c("black","red"), lty = c(1, 2), horiz = TRUE)
```




### Utility of KS test---Gamma Distributions
```{r}

## add extra space to right margin of plot within frame
par(mar = c(9, 4.1, 3.1, 6.5), xpd = TRUE)
plot(nvec, data_powertest$Gamma.KS, axes=FALSE, ylim=c(0,1), xlab="", ylab="", 
   type="o", lwd = 2, col="black", main="Utility of SW test ... LogNormal Samples")
axis(2, ylim=c(0,1),col="black",las=1)  
mtext("Power of KS test",side=2,line=2.5)
box()
par(new=TRUE)

## Plot the second plot and put axis scale on right
plot(nvec, data_powerloss$Gamma.0.5,  xlab="", ylab="", ylim=c(-0.01,0.1), 
    axes=FALSE, type="l", lty = 2, lwd = 2, col="red")
mtext("Power loss of t test",side=4,col="black",line=4) 
axis(4, ylim=c(0,0.5), col="red",col.axis="black",las=1)
## a little farther out (line=4) to make room for labels
axis(4, ylim=c(0,0.2), col="blue",col.axis="blue",las=1)

## Draw the time axis
axis(1,pretty(range(nvec),10))
mtext("Sample Size",side=1,col="black",line=2.5)  
## Add Legend
legend("bottom", inset = c(0, -0.3), legend=c("power of KS test","powerloss of t test"),
  col=c("black","red"), lty = c(1, 2), horiz = TRUE)
```



### Utility of KS test---Normal Distributions
```{r}

## add extra space to right margin of plot within frame
par(mar = c(9, 4.1, 3.1, 6.5), xpd = TRUE)
plot(nvec, data_powertest$Standard.Normal.KS, axes=FALSE, ylim=c(0,1), xlab="", ylab="", 
   type="o", lwd = 2, col="black", main="Utility of SW test ... Normal Samples")
axis(2, ylim=c(0,1),col="black",las=1)  
mtext("Power of KS test",side=2,line=2.5)
box()
par(new=TRUE)

## Plot the second plot and put axis scale on right
plot(nvec, data_powerloss$Standard.Normal.0.5,  xlab="", ylab="", ylim=c(-0.01,0.1), 
    axes=FALSE, type="l", lty = 2, lwd = 2, col="red")
mtext("Power loss of t test",side=4,col="black",line=4) 
axis(4, ylim=c(0,0.5), col="red",col.axis="black",las=1)
## a little farther out (line=4) to make room for labels
axis(4, ylim=c(0,0.2), col="blue",col.axis="blue",las=1)

## Draw the time axis
axis(1,pretty(range(nvec),10))
mtext("Sample Size",side=1,col="black",line=2.5)  
## Add Legend
legend("bottom", inset = c(0, -0.3), legend=c("power of KS test","powerloss of t test"),
  col=c("black","red"), lty = c(1, 2), horiz = TRUE)
```



### Utility of KS test---t Distributions
```{r}

## add extra space to right margin of plot within frame
par(mar = c(9, 4.1, 3.1, 6.5), xpd = TRUE)
plot(nvec, data_powertest$t.KS, axes=FALSE, ylim=c(0,1), xlab="", ylab="", 
   type="o", lwd = 2, col="black", main="Utility of SW test ... t Samples")
axis(2, ylim=c(0,1),col="black",las=1)  
mtext("Power of KS test",side=2,line=2.5)
box()
par(new=TRUE)

## Plot the second plot and put axis scale on right
plot(nvec, data_powerloss$t.0.5,  xlab="", ylab="", ylim=c(-0.01,0.1), 
    axes=FALSE, type="l", lty = 2, lwd = 2, col="red")
mtext("Power loss of t test",side=4,col="black",line=4) 
axis(4, ylim=c(0,0.5), col="red",col.axis="black",las=1)
## a little farther out (line=4) to make room for labels
axis(4, ylim=c(0,0.2), col="blue",col.axis="blue",las=1)

## Draw the time axis
axis(1,pretty(range(nvec),10))
mtext("Sample Size",side=1,col="black",line=2.5)  
## Add Legend
legend("bottom", inset = c(0, -0.3), legend=c("power of KS test","powerloss of t test"),
  col=c("black","red"), lty = c(1, 2), horiz = TRUE)
```


### Utility of KS test---Uniform Distributions
```{r}

## add extra space to right margin of plot within frame
par(mar = c(9, 4.1, 3.1, 6.5), xpd = TRUE)
plot(nvec, data_powertest$Uniform.KS, axes=FALSE, ylim=c(0,1), xlab="", ylab="", 
   type="o", lwd = 2, col="black", main="Utility of SW test ... Uniform Samples")
axis(2, ylim=c(0,1),col="black",las=1)  
mtext("Power of KS test",side=2,line=2.5)
box()
par(new=TRUE)

## Plot the second plot and put axis scale on right
plot(nvec, data_powerloss$Uniform.0.5,  xlab="", ylab="", ylim=c(-0.01,0.1), 
    axes=FALSE, type="l", lty = 2, lwd = 2, col="red")
mtext("Power loss of t test",side=4,col="black",line=4) 
axis(4, ylim=c(0,0.5), col="red",col.axis="black",las=1)
## a little farther out (line=4) to make room for labels
axis(4, ylim=c(0,0.2), col="blue",col.axis="blue",las=1)

## Draw the time axis
axis(1,pretty(range(nvec),10))
mtext("Sample Size",side=1,col="black",line=2.5)  
## Add Legend
legend("bottom", inset = c(0, -0.3), legend=c("power of KS test","powerloss of t test"),
  col=c("black","red"), lty = c(1, 2), horiz = TRUE)
```



### Utility of JB test---Exponential Distributions
```{r}
## add extra space to right margin of plot within frame
par(mar = c(9, 4.1, 3.1, 6.5), xpd = TRUE)
plot(nvec, data_powertest$Exponential.JB, axes=FALSE, ylim=c(0,1), xlab="", ylab="", 
   type="o", lwd = 2, col="black", main="Utility of JB test ... Exponential Samples")
axis(2, ylim=c(0,1),col="black",las=1)  
mtext("Power of JB test",side=2,line=2.5)
box()
par(new=TRUE)

## Plot the second plot and put axis scale on right
plot(nvec, data_powerloss$Exponential.0.5,  xlab="", ylab="", ylim=c(-0.01,0.1), 
    axes=FALSE, type="l", lty = 2, lwd = 2, col="red")
mtext("Power loss of t test",side=4,col="black",line=4) 
axis(4, ylim=c(0,0.5), col="red",col.axis="black",las=1)
## a little farther out (line=4) to make room for labels
axis(4, ylim=c(0,0.2), col="blue",col.axis="blue",las=1)

## Draw the time axis
axis(1,pretty(range(nvec),10))
mtext("Sample Size",side=1,col="black",line=2.5)  
## Add Legend
legend("bottom", inset = c(0, -0.3), legend=c("power of JB test","powerloss of t test"),
  col=c("black","red"), lty = c(1, 2), horiz = TRUE)

```


### Utility of JB test---LogNormal Distributions
```{r}

## add extra space to right margin of plot within frame
par(mar = c(9, 4.1, 3.1, 6.5), xpd = TRUE)
plot(nvec, data_powertest$LogNormal.JB, axes=FALSE, ylim=c(0,1), xlab="", ylab="", 
   type="o", lwd = 2, col="black", main="Utility of JB test ... LogNormal Samples")
axis(2, ylim=c(0,1),col="black",las=1)  
mtext("Power of JB test",side=2,line=2.5)
box()
par(new=TRUE)

## Plot the second plot and put axis scale on right
plot(nvec, data_powerloss$LogNormal.0.5,  xlab="", ylab="", ylim=c(-0.01,0.1), 
    axes=FALSE, type="l", lty = 2, lwd = 2, col="red")
mtext("Power loss of t test",side=4,col="black",line=4) 
axis(4, ylim=c(0,0.5), col="red",col.axis="black",las=1)
## a little farther out (line=4) to make room for labels
axis(4, ylim=c(0,0.2), col="blue",col.axis="blue",las=1)

## Draw the time axis
axis(1,pretty(range(nvec),10))
mtext("Sample Size",side=1,col="black",line=2.5)  
## Add Legend
legend("bottom", inset = c(0, -0.3), legend=c("power of JB test","powerloss of t test"),
  col=c("black","red"), lty = c(1, 2), horiz = TRUE)
```


### Utility of JB test---Chi-Square Distributions
```{r}

## add extra space to right margin of plot within frame
par(mar = c(9, 4.1, 3.1, 6.5), xpd = TRUE)
plot(nvec, data_powertest$Chi.Square.JB, axes=FALSE, ylim=c(0,1), xlab="", ylab="", 
   type="o", lwd = 2, col="black", main="Utility of JB test ... Chi-Square Samples")
axis(2, ylim=c(0,1),col="black",las=1)  
mtext("Power of SW test",side=2,line=2.5)
box()
par(new=TRUE)

## Plot the second plot and put axis scale on right
plot(nvec, data_powerloss$Chi.Square.0.5,  xlab="", ylab="", ylim=c(-0.01,0.1), 
    axes=FALSE, type="l", lty = 2, lwd = 2, col="red")
mtext("Power loss of t test",side=4,col="black",line=4) 
axis(4, ylim=c(0,0.5), col="red",col.axis="black",las=1)
## a little farther out (line=4) to make room for labels
axis(4, ylim=c(0,0.2), col="blue",col.axis="blue",las=1)

## Draw the time axis
axis(1,pretty(range(nvec),10))
mtext("Sample Size",side=1,col="black",line=2.5)  
## Add Legend
legend("bottom", inset = c(0, -0.3), legend=c("power of JB test","powerloss of t test"),
  col=c("black","red"), lty = c(1, 2), horiz = TRUE)
```



### Utility of JB test---Weibull Distributions
```{r}

## add extra space to right margin of plot within frame
par(mar = c(9, 4.1, 3.1, 6.5), xpd = TRUE)
plot(nvec, data_powertest$Weibull.JB, axes=FALSE, ylim=c(0,1), xlab="", ylab="", 
   type="o", lwd = 2, col="black", main="Utility of JB test ... Weibull Samples")
axis(2, ylim=c(0,1),col="black",las=1)  
mtext("Power of JB test",side=2,line=2.5)
box()
par(new=TRUE)

## Plot the second plot and put axis scale on right
plot(nvec, data_powerloss$Weibull.0.5,  xlab="", ylab="", ylim=c(-0.01,0.1), 
    axes=FALSE, type="l", lty = 2, lwd = 2, col="red")
mtext("Power loss of t test",side=4,col="black",line=4) 
axis(4, ylim=c(0,0.5), col="red",col.axis="black",las=1)
## a little farther out (line=4) to make room for labels
axis(4, ylim=c(0,0.2), col="blue",col.axis="blue",las=1)

## Draw the time axis
axis(1,pretty(range(nvec),10))
mtext("Sample Size",side=1,col="black",line=2.5)  
## Add Legend
legend("bottom", inset = c(0, -0.3), legend=c("power of JB test","powerloss of t test"),
  col=c("black","red"), lty = c(1, 2), horiz = TRUE)
```




### Utility of JB test---Gamma Distributions
```{r}

## add extra space to right margin of plot within frame
par(mar = c(9, 4.1, 3.1, 6.5), xpd = TRUE)
plot(nvec, data_powertest$Gamma.JB, axes=FALSE, ylim=c(0,1), xlab="", ylab="", 
   type="o", lwd = 2, col="black", main="Utility of JB test ... LogNormal Samples")
axis(2, ylim=c(0,1),col="black",las=1)  
mtext("Power of JB test",side=2,line=2.5)
box()
par(new=TRUE)

## Plot the second plot and put axis scale on right
plot(nvec, data_powerloss$Gamma.0.5,  xlab="", ylab="", ylim=c(-0.01,0.1), 
    axes=FALSE, type="l", lty = 2, lwd = 2, col="red")
mtext("Power loss of t test",side=4,col="black",line=4) 
axis(4, ylim=c(0,0.5), col="red",col.axis="black",las=1)
## a little farther out (line=4) to make room for labels
axis(4, ylim=c(0,0.2), col="blue",col.axis="blue",las=1)

## Draw the time axis
axis(1,pretty(range(nvec),10))
mtext("Sample Size",side=1,col="black",line=2.5)  
## Add Legend
legend("bottom", inset = c(0, -0.3), legend=c("power of JB test","powerloss of t test"),
  col=c("black","red"), lty = c(1, 2), horiz = TRUE)
```



### Utility of JB test---Normal Distributions
```{r}

## add extra space to right margin of plot within frame
par(mar = c(9, 4.1, 3.1, 6.5), xpd = TRUE)
plot(nvec, data_powertest$Standard.Normal.JB, axes=FALSE, ylim=c(0,1), xlab="", ylab="", 
   type="o", lwd = 2, col="black", main="Utility of JB test ... Normal Samples")
axis(2, ylim=c(0,1),col="black",las=1)  
mtext("Power of JB test",side=2,line=2.5)
box()
par(new=TRUE)

## Plot the second plot and put axis scale on right
plot(nvec, data_powerloss$Standard.Normal.0.5,  xlab="", ylab="", ylim=c(-0.01,0.1), 
    axes=FALSE, type="l", lty = 2, lwd = 2, col="red")
mtext("Power loss of t test",side=4,col="black",line=4) 
axis(4, ylim=c(0,0.5), col="red",col.axis="black",las=1)
## a little farther out (line=4) to make room for labels
axis(4, ylim=c(0,0.2), col="blue",col.axis="blue",las=1)

## Draw the time axis
axis(1,pretty(range(nvec),10))
mtext("Sample Size",side=1,col="black",line=2.5)  
## Add Legend
legend("bottom", inset = c(0, -0.3), legend=c("power of JB test","powerloss of t test"),
  col=c("black","red"), lty = c(1, 2), horiz = TRUE)
```



### Utility of JB test---t Distributions
```{r}

## add extra space to right margin of plot within frame
par(mar = c(9, 4.1, 3.1, 6.5), xpd = TRUE)
plot(nvec, data_powertest$t.JB, axes=FALSE, ylim=c(0,1), xlab="", ylab="", 
   type="o", lwd = 2, col="black", main="Utility of JB test ... t Samples")
axis(2, ylim=c(0,1),col="black",las=1)  
mtext("Power of JB test",side=2,line=2.5)
box()
par(new=TRUE)

## Plot the second plot and put axis scale on right
plot(nvec, data_powerloss$t.0.5,  xlab="", ylab="", ylim=c(-0.01,0.1), 
    axes=FALSE, type="l", lty = 2, lwd = 2, col="red")
mtext("Power loss of t test",side=4,col="black",line=4) 
axis(4, ylim=c(0,0.5), col="red",col.axis="black",las=1)
## a little farther out (line=4) to make room for labels
axis(4, ylim=c(0,0.2), col="blue",col.axis="blue",las=1)

## Draw the time axis
axis(1,pretty(range(nvec),10))
mtext("Sample Size",side=1,col="black",line=2.5)  
## Add Legend
legend("bottom", inset = c(0, -0.3), legend=c("power of JB test","powerloss of t test"),
  col=c("black","red"), lty = c(1, 2), horiz = TRUE)
```


### Utility of JB test---Uniform Distributions
```{r}

## add extra space to right margin of plot within frame
par(mar = c(9, 4.1, 3.1, 6.5), xpd = TRUE)
plot(nvec, data_powertest$Uniform.JB, axes=FALSE, ylim=c(0,1), xlab="", ylab="", 
   type="o", lwd = 2, col="black", main="Utility of JB test ... Uniform Samples")
axis(2, ylim=c(0,1),col="black",las=1)  
mtext("Power of JB test",side=2,line=2.5)
box()
par(new=TRUE)

## Plot the second plot and put axis scale on right
plot(nvec, data_powerloss$Uniform.0.5,  xlab="", ylab="", ylim=c(-0.01,0.1), 
    axes=FALSE, type="l", lty = 2, lwd = 2, col="red")
mtext("Power loss of t test",side=4,col="black",line=4) 
axis(4, ylim=c(0,0.5), col="red",col.axis="black",las=1)
## a little farther out (line=4) to make room for labels
axis(4, ylim=c(0,0.2), col="blue",col.axis="blue",las=1)

## Draw the time axis
axis(1,pretty(range(nvec),10))
mtext("Sample Size",side=1,col="black",line=2.5)  
## Add Legend
legend("bottom", inset = c(0, -0.3), legend=c("power of JB test","powerloss of t test"),
  col=c("black","red"), lty = c(1, 2), horiz = TRUE)
```