---
title: "simultaneous confidence bands for Q-Q plot"
author: "Benedict Kongyir"
date: "`r format(Sys.time(), '%m/%d/%Y')`"
output: 
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.height = 12, fig.width = 12, warning = FALSE, message = FALSE, verbose = FALSE)
rm(list = ls())
if(!require("pacman")) install.packages("pacman")
pacman::p_load(ggplot2, qqplotr)
```


### Function to compute simultaneous confidence bands for Q-Q plot
```{r}

# Function to compute simultaneous confidence bands for Q-Q plot
qq_plot_with_simultaneous_ci <- function(data, title = "Q-Q Plot with Simultaneous Confidence Bands", B = 1e4, conf_level = 0.95) {
  n <- length(data)
 
  sorted_data <- sort(data)  # Sort the sample data
  theoretical_quantiles <- qnorm(ppoints(n))  # Theoretical quantiles under normality
  
  # Bootstrap to construct confidence bands
  boot_samples <- replicate(B, sort(rnorm(n)))
  lower_band <- apply(boot_samples, 1, function(x) quantile(x, (1 - conf_level) / 2))
  upper_band <- apply(boot_samples, 1, function(x) quantile(x, 1 - (1 - conf_level) / 2))
  
  # Create a data frame
  df <- data.frame(Theoretical = theoretical_quantiles, Sample = sorted_data,
                   Lower = lower_band, Upper = upper_band)
  
  # Create the Q-Q plot with confidence bands
  p <- ggplot(df, aes(x = Theoretical, y = Sample)) +
    geom_point(color = "black") +  # Q-Q points
    geom_abline(slope = 1, intercept = 0, color = "red", linetype = "dashed") +  # Reference line
    geom_ribbon(aes(ymin = Lower, ymax = Upper), fill = "blue", alpha = 0.2) +  # Simultaneous CI bands
    theme_minimal() +
    labs(title = title, x = "Theoretical Quantiles (Normal)", y = "Sample Quantiles")
  
  print(p)
}

```

### Examples, normally distributed sample N(0, 1)
```{r}
# Example usage with a normally distributed sample
set.seed(12345)
x <- rnorm(50, mean = 0, sd = 1)  # Normal data
sample_data <- scale(x, center = TRUE, scale = TRUE)
qq_plot_with_simultaneous_ci(sample_data)
```


### Example usage with a normally distributed sample N( 50, 50, 16)
```{r}
set.seed(123)
x <- rnorm(50, mean = 50, sd = 16)  # Normal data
sample_data <- scale(x, center = TRUE, scale = TRUE)
qq_plot_with_simultaneous_ci(sample_data)

```

### Example usage with a non-normal sample t(3) for n = 50
```{r}
# Example usage with a non-normal sample
x <- rt(50, df = 3)  # Heavy-tailed t-distribution
sample_data_non_normal <- scale(x, center = TRUE, scale = TRUE)
qq_plot_with_simultaneous_ci(sample_data_non_normal)

```


### Example usage with a non-normal sample Exp(3) for n=50
```{r}
# Example usage with a non-normal sample
x <- rexp(50, rate = 3)  # Heavy-tailed t-distribution
sample_data_non_normal <- scale(x, center = TRUE, scale = TRUE)
qq_plot_with_simultaneous_ci(sample_data_non_normal)

```


### Example usage with a normally distributed sample N( 10, 50, 16)
```{r}
set.seed(123)
x <- rnorm(10, mean = 50, sd = 16)  # Normal data
sample_data <- scale(x, center = TRUE, scale = TRUE)
qq_plot_with_simultaneous_ci(sample_data)

```

### Example usage with a non-normal sample t(3) for n= 10
```{r}
# Example usage with a non-normal sample
x <- rt(10, df = 3)  # Heavy-tailed t-distribution
sample_data_non_normal <- scale(x, center = TRUE, scale = TRUE)
qq_plot_with_simultaneous_ci(sample_data_non_normal)

```


### Example usage with a non-normal sample Exp(3) for n=10
```{r}
# Example usage with a non-normal sample
x <- rexp(10, rate = 3)  # Heavy-tailed t-distribution
sample_data_non_normal <- scale(x, center = TRUE, scale = TRUE)
qq_plot_with_simultaneous_ci(sample_data_non_normal)

```

```{r}
# # Load necessary libraries
# library(ggplot2)
# 
# # Function to compute simultaneous confidence bands for Q-Q plot using Beta distribution
# qq_plot_with_simultaneous_ci <- function(data, title = "Q-Q Plot with Simultaneous Confidence Bands", conf_level = 0.95) {
#   # Standardize the data to have mean 0 and sd 1
#   data <- as.vector(scale(data))
#   n <- length(data)
#   sorted_data <- sort(data)
#   theoretical_quantiles <- qnorm(ppoints(n))
#   
#   # Compute adjusted alpha for Šidák correction
#   alpha <- 1 - conf_level
#   adjusted_alpha <- 1 - (1 - alpha)^(1/n)
#   
#   # Calculate Beta quantiles for each order statistic
#   i <- 1:n
#   lower_beta <- qbeta(adjusted_alpha / 2, i, n - i + 1)
#   upper_beta <- qbeta(1 - adjusted_alpha / 2, i, n - i + 1)
#   
#   # Convert Beta quantiles to Normal quantiles
#   lower_band <- qnorm(lower_beta)
#   upper_band <- qnorm(upper_beta)
#   
#   # Create data frame for plotting
#   df <- data.frame(Theoretical = theoretical_quantiles, Sample = sorted_data,
#                    Lower = lower_band, Upper = upper_band)
#   
#   # Generate the Q-Q plot with simultaneous confidence bands
#   p <- ggplot(df, aes(x = Theoretical, y = Sample)) +
#     geom_point(color = "black") +
#     geom_abline(slope = 1, intercept = 0, color = "red", linetype = "dashed") +
#     geom_ribbon(aes(ymin = Lower, ymax = Upper), fill = "blue", alpha = 0.2) +
#     theme_minimal() +
#     labs(title = title, x = "Theoretical Quantiles (Normal)", y = "Sample Quantiles")
#   
#   print(p)
# }
# 
# # Example usage with a small normal sample
# set.seed(123)
# x <- rnorm(100)
# qq_plot_with_simultaneous_ci(x)
# 
# # Example usage with a small non-normal sample
# x <- rexp(100, rate = 3)
# qq_plot_with_simultaneous_ci(x)
```

