---
title: "Density plots of one sample t test statistic"
author: "Benedict Kongyir"
date: "`r format(Sys.time(), '%m/%d/%Y')`"
output: 
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## One sample case

```{r}
rm(list = ls())
setwd("/Users/benedictkongyir/Desktop/OSU/Research/Pretest-Simulation/Simulation/PLOT OF TEST STAT UNDER H0")
load("/Users/benedictkongyir/Desktop/OSU/Research/Pretest-Simulation/Simulation/PLOT OF TEST STAT UNDER H0/one_samples_plots.RData")
set.seed(12345)
```

### Combine Plots
```{r, fig.height= 14, fig.width= 10}
par(mfrow = c(4,2))
# Adjust margins to reduce space between plots
par(mai = c(0.95, 0.85, 0.3, 0.3))  # Adjust as needed
par(cex.lab = 1.5, font.lab = 2, cex.axis = 1.2, cex.main = 1.5, cex.sub = 1.2)  # Larger and bold
df = n - 1
z <- seq(from = -3, to = 3, by = 0.01)
# normal Distribution
plot(z, dt(z, df = df), col = "red", type = "l", xlab = " ",  ylab = "Density",  lwd = 2, main = " ", sub = " ")
title(main = "Density plots of t_18 and N(0,1)",sub = substitute(paste(bold("normal Dist"))),  cex = 2)
lines(density(norm_statistic), lwd = 2)
abline(v=qt(0.025, df = df), col = "blue")
abline(v=qt(0.975, df = df), col = "blue")
legend("bottom", legend = c("theoretical", "empirical"), col = c("red", "black"), lty = 1, cex = 1, text.font = 2, lwd = 2, bty = "n", ncol=2, inset=c(0, -.22), xpd=TRUE)

# Exponential Distribution
plot(z, dt(z, df = df), col = "red",type = "l", lwd = 2, main = " ", sub = " " , xlab = " ",  ylab = "Density")
title(main = "Density plots of t_18 and exp(1)", sub = substitute(paste(bold("Exponential Dist"))),  cex = 2)
lines(density(e_statistic) , lwd = 2)
abline(v=qt(0.025, df = df), col = "blue")
abline(v=qt(0.975, df = df), col = "blue")
legend("bottom", legend = c("theoretical", "empirical"), col = c("red", "black"), lty = 1, cex = 1, text.font = 2, lwd = 2, bty = "n", ncol=2, inset=c(0, -.22), xpd=TRUE)

# t Distribution
plot(z, dt(z, df = df), col = "red", type = "l", lwd = 2, main = " ", sub = " " , xlab = " ",  ylab = "Density")
title(main = "Density plots of t_18 and t(3)", sub = substitute(paste(bold("t Dist"))),  cex = 2)
lines(density(t_statistic) , lwd = 2)
abline(v=qt(0.025, df = df), col = "blue")
abline(v=qt(0.975, df = df), col = "blue")
legend("bottom", legend = c("theoretical", "empirical"), col = c("red", "black"), lty = 1, cex = 1, text.font = 2, lwd = 2, bty = "n", ncol=2, inset=c(0, -.22), xpd=TRUE)

# uniform Distribution
plot(z, dt(z, df = df), col = "red",  type = "l", lwd = 2, main = " ", sub = " " , xlab = " ",  ylab = "Density")
title(main = "Density plots of t_18 and U(0,1)", sub = substitute(paste(bold("Uniform Dist"))),  cex = 2)
lines(density(u_statistic) , lwd = 2)
abline(v=qt(0.025, df = df), col = "blue")
abline(v=qt(0.975, df = df), col = "blue")
legend("bottom", legend = c("theoretical", "empirical"), col = c("red", "black"), lty = 1, cex = 1, text.font = 2, lwd = 2, bty = "n", ncol=2, inset=c(0, -.22), xpd=TRUE)

# chi-squared Distribution
plot(z, dt(z, df = df), col = "red",  type = "l", lwd = 2, main = " ", sub = " " , xlab = " ",  ylab = "Density")
title(main = "Density plots of t_18 and Chisq(7)",  sub = substitute(paste(bold("Chi-Square Dist"))),  cex = 2)
lines(density(k_statistic) , lwd = 2)
abline(v=qt(0.025, df = df), col = "blue")
abline(v=qt(0.975, df = df ), col = "blue")
legend("bottom", legend = c("theoretical", "empirical"), col = c("red", "black"), lty = 1, cex = 1, text.font = 2, lwd = 2, bty = "n", ncol=2, inset=c(0, -.22), xpd=TRUE)

# weibull Distribution
plot(z, dt(z, df = df), col = "red" , type = "l", lwd = 2, main = " ", sub = " " , xlab = " ",  ylab = "Density")
title(main = "Density plots of t_18 and Weibull(1, 2)", sub = substitute(paste(bold("Weibull Dist"))),  cex = 2)
lines(density(w_statistic) , lwd = 2)
abline(v=qt(0.025, df = df ), col = "blue")
abline(v=qt(0.975, df = df ), col = "blue")
legend("bottom", legend = c("theoretical", "empirical"), col = c("red", "black"), lty = 1, cex = 1, text.font = 2, lwd = 2, bty = "n", ncol=2, inset=c(0, -.22), xpd=TRUE)

# gamma Distribution
plot(z, dt(z, df = df), col = "red" , type = "l", lwd = 2, main = " ", sub = " " , xlab = " ",  ylab = "Density")
title(main = "Density plots of t_18 and Gamma(3,0.1)", sub = substitute(paste(bold("Gamma Dist"))),  cex = 2)
lines(density(g_statistic) , lwd = 2)
abline(v=qt(0.025, df = df), col = "blue")
abline(v=qt(0.975, df = df), col = "blue")
legend("bottom", legend = c("theoretical", "empirical"), col = c("red", "black"), lty = 1, cex = 1, text.font = 2, lwd = 2, bty = "n", ncol=2, inset=c(0, -.22), xpd=TRUE)

# lognormal Distribution
plot(z, dt(z, df = df), col = "red" , type = "l", lwd = 2, main = " ", sub = " " , xlab = " ",  ylab = "Density")
title(main = "Density plots of t_18 and logN(0,1)", sub = substitute(paste(bold("Lognormal Dist"))),  cex = 2)
lines(density(log_statistic), lwd = 2)
abline(v=qt(0.025, df = df), col = "blue")
abline(v=qt(0.975, df = df), col = "blue")
legend("bottom", legend = c("theoretical ", "empirical"), col = c("red", "black"), lty = 1, cex = 1, text.font = 2, lwd = 3, bty = "n", ncol=2, inset=c(0, -.22), xpd=TRUE)


```


### normal Distribution
The distribution of the t test statistic for samples taken from a normal distribution approximately follows the t distribution as show in the plot below. This supports the controlled Type I error rate shown in the table above.
```{r}
df = n - 1
z <- seq(from = -3, to = 3, by = 0.01)
# normal Distribution
plot(z, dt(z, df = df), col = "red", type = "l", xlab = " ",  ylab = "Density",  lwd = 2, main = " ", sub = " ")
title(main = "Density plots of t_18 and N(0,1)", sub = "normal Dist")
lines(density(norm_statistic), lwd = 2)
abline(v=qt(0.025, df = df), col = "blue")
abline(v=qt(0.975, df = df), col = "blue")
legend("bottom", legend = c("theoretical t density", "empirical t density"), col = c("red", "black"), lty = 1, cex = 0.75, text.font = 2, lwd = 2, bty = "n", ncol=2, inset=c(0, -.22), xpd=TRUE)
```

### Exponential Distribution
The distribution of the t test statistic for samples taken from exponential distribution deviates from the t distribution. It has a fatter tail to the left and slimmer tail to the right as show in the plot below. This supports the inflated Type I error rate shown in the table above.
```{r}
# Exponential Distribution
plot(z, dt(z, df = df), col = "red",type = "l", lwd = 2, main = " ", sub = " " , xlab = " ",  ylab = "Density")
title(main = "Density plots of t_18 and exp(1)", sub = "Exponential Dist")
lines(density(e_statistic) , lwd = 2)
abline(v=qt(0.025, df = df), col = "blue")
abline(v=qt(0.975, df = df), col = "blue")
legend("bottom", legend = c("theoretical t density", "empirical t density"), col = c("red", "black"), lty = 1, cex = 0.75, text.font = 2, lwd = 2, bty = "n", ncol=2, inset=c(0, -.22), xpd=TRUE)

```

### t Distribution
The distribution of the t test statistic for samples taken from t distribution is approximately follows the t distribution except that it has a flatter top. The tails are similar to that of the t distribution as show in the plot below. This supports the controlled Type I error rate shown in the table above.
```{r}
# t Distribution
plot(z, dt(z, df = df), col = "red", type = "l", lwd = 2, main = " ", sub = " " , xlab = " ",  ylab = "Density")
title(main = "Density plots of t_18 and t(3)", sub = "t Dist")
lines(density(t_statistic) , lwd = 2)
abline(v=qt(0.025, df = df), col = "blue")
abline(v=qt(0.975, df = df), col = "blue")
legend("bottom", legend = c("theoretical t density", "empirical t density"), col = c("red", "black"), lty = 1, cex = 0.75, text.font = 2, lwd = 2, bty = "n", ncol=2, inset=c(0, -.22), xpd=TRUE)
```

### Uniform Distribution
The distribution of the t test statistic for samples taken from t distribution is approximately follows the t distribution. The tails are similar to that of the t distribution as show in the plot below. This supports the controlled Type I error rate shown in the table above.
```{r}
# uniform Distribution
plot(z, dt(z, df = df), col = "red",  type = "l", lwd = 2, main = " ", sub = " " , xlab = " ",  ylab = "Density")
title(main = "Density plots of t_18 and U(0,1)", sub = "Uniform Dist")
lines(density(u_statistic) , lwd = 2)
abline(v=qt(0.025, df = df), col = "blue")
abline(v=qt(0.975, df = df), col = "blue")
legend("bottom", legend = c("theoretical t density", "empirical t density"), col = c("red", "black"), lty = 1, cex = 0.75, text.font = 2, lwd = 2, bty = "n", ncol=2, inset=c(0, -.22), xpd=TRUE)
```


### chi-squared Distribution
The distribution of the t test statistic for samples taken from Chi-Squared distribution deviates from the t distribution. It has a fatter tail to the left and slimmer tail to the right as show in the plot below. This supports the inflated Type I error rate shown in the table above.
```{r}
# chi-squared Distribution
plot(z, dt(z, df = df), col = "red",  type = "l", lwd = 2, main = " ", sub = " " , xlab = " ",  ylab = "Density")
title(main = "Density plots of t_18 and Chisq(7)", sub = "Chi-Square Dist")
lines(density(k_statistic) , lwd = 2)
abline(v=qt(0.025, df = df), col = "blue")
abline(v=qt(0.975, df = df ), col = "blue")
legend("bottom", legend = c("theoretical t density", "empirical t density"), col = c("red", "black"), lty = 1, cex = 0.75, text.font = 2, lwd = 2, bty = "n", ncol=2, inset=c(0, -.22), xpd=TRUE)
```

### Weibull Distribution
The distribution of the t test statistic for samples taken from Weibull distribution deviates from the t distribution. It has a fatter tail to the left and slimmer tail to the right as show in the plot below.This supports the inflated Type I error rate shown in the table above.
```{r}
# weibull Distribution
plot(z, dt(z, df = df), col = "red" , type = "l", lwd = 2, main = " ", sub = " " , xlab = " ",  ylab = "Density")
title(main = "Density plots of t_18 and Weibull(1, 2)", sub = "Weibull Dist")
lines(density(w_statistic) , lwd = 2)
abline(v=qt(0.025, df = df ), col = "blue")
abline(v=qt(0.975, df = df ), col = "blue")
legend("bottom", legend = c("theoretical t density", "empirical t density"), col = c("red", "black"), lty = 1, cex = 0.75, text.font = 2, lwd = 2, bty = "n", ncol=2, inset=c(0, -.22), xpd=TRUE)

```


### Gamma Distribution
The distribution of the t test statistic for samples taken from Gamma distribution deviates from the t distribution. It has a fatter tail to the left and slimmer tail to the right as show in the plot below. This supports the inflated Type I error rate shown in the table above.
```{r}
# gamma Distribution
plot(z, dt(z, df = df), col = "red" , type = "l", lwd = 2, main = " ", sub = " " , xlab = " ",  ylab = "Density")
title(main = "Density plots of t_18 and Gamma(3,0.1)", sub = "Gamma Dist")
lines(density(g_statistic) , lwd = 2)
abline(v=qt(0.025, df = df), col = "blue")
abline(v=qt(0.975, df = df), col = "blue")
legend("bottom", legend = c("theoretical t density", "empirical t density"), col = c("red", "black"), lty = 1, cex = 0.75, text.font = 2, lwd = 2, bty = "n", ncol=2, inset=c(0, -.22), xpd=TRUE)

```


### Lognormal Distribution
The distribution of the t test statistic for samples taken from Log normal distribution deviates much from the t distribution. It has a fatter tail to the left and slimmer tail to the right as show in the plot below. This explains why we have extreme inflation of Type I error rate for the one-sample t test for lognormal samples.
```{r}
# lognormal Distribution
plot(z, dt(z, df = df), col = "red" , type = "l", lwd = 2, main = " ", sub = " " , xlab = " ",  ylab = "Density")
title(main = "Density plots of t_18 and logN(0,1)", sub = "Lognormal Dist")
lines(density(log_statistic), lwd = 2)
abline(v=qt(0.025, df = df), col = "blue")
abline(v=qt(0.975, df = df), col = "blue")
legend("bottom", legend = c("theoretical t density", "empirical t density"), col = c("red", "black"), lty = 1, cex = 0.75, text.font = 2, lwd = 2, bty = "n", ncol=2, inset=c(0, -.22), xpd=TRUE)

```

### Estimated Type I errors

```{r}
# power of SW test
errors <-c( Type1_error_norm, Type1_error_e, Type1_error_t, Type1_error_u,Type1_error_k,Type1_error_w, Type1_error_g,Type1_error_l)
dist <-c("normal", "exponential", "t", "uniform", "chi-squared", "weillbul", "gamma", "lognormal")

# put data in a table
kk <- data.frame(dist, errors)
knitr::kable(kk, caption = "Estimated Type I errors")
```


### Explanation of Results

The theoretical and empirical density plots of the two-sample t test confirms the popular belief that  Type I error rates is inflated for asymmetric distributions like exponential, chi-square, lognormal etc, but controlled for symmetric distributions like normal, uniform, and t. 

