---
title: "Density plots of two sample t test statistic"
author: "Benedict Kongyir"
date: "`r format(Sys.time(), '%m/%d/%Y')`"
output: 
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    code_folding: hide
    bibliography: ref.bib
link-citations: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
rm(list = ls())
setwd("/Users/benedictkongyir/Desktop/OSU/Research/Pretest-Simulation/Simulation/PLOT OF TEST STAT UNDER H0")
load("/Users/benedictkongyir/Desktop/OSU/Research/Pretest-Simulation/Simulation/PLOT OF TEST STAT UNDER H0/two_samples_plots.RData")
set.seed(12345)
```

### Combine Plots
```{r, fig.height= 14, fig.width= 10}
par(mfrow = c(4,2))
# Adjust margins to reduce space between plots
par(mai = c(0.95, 0.85, 0.3, 0.3))  # Adjust as needed
par(cex.lab = 1.5, font.lab = 2, cex.axis = 1.2, cex.main = 1.5, cex.sub = 1.2)  # Larger and bold
df = n - 1
z <- seq(from = -3, to = 3, by = 0.01)
# normal Distribution
plot(z, dt(z, df = df), col = "red", type = "l", xlab = " ",  ylab = "Density",  lwd = 2, main = " ", sub = " ")
title(main = "Density plots of t_18 and N(0,1)",sub = substitute(paste(bold("normal Dist"))),  cex = 2)
lines(density(norm_statistic), lwd = 2)
abline(v=qt(0.025, df = df), col = "blue")
abline(v=qt(0.975, df = df), col = "blue")
legend("bottom", legend = c("theoretical", "empirical"), col = c("red", "black"), lty = 1, cex = 1, text.font = 2, lwd = 2, bty = "n", ncol=2, inset=c(0, -.22), xpd=TRUE)

# Exponential Distribution
plot(z, dt(z, df = df), col = "red",type = "l", lwd = 2, main = " ", sub = " " , xlab = " ",  ylab = "Density")
title(main = "Density plots of t_18 and exp(1)", sub = substitute(paste(bold("Exponential Dist"))),  cex = 2)
lines(density(e_statistic) , lwd = 2)
abline(v=qt(0.025, df = df), col = "blue")
abline(v=qt(0.975, df = df), col = "blue")
legend("bottom", legend = c("theoretical", "empirical"), col = c("red", "black"), lty = 1, cex = 1, text.font = 2, lwd = 2, bty = "n", ncol=2, inset=c(0, -.22), xpd=TRUE)

# t Distribution
plot(z, dt(z, df = df), col = "red", type = "l", lwd = 2, main = " ", sub = " " , xlab = " ",  ylab = "Density")
title(main = "Density plots of t_18 and t(3)", sub = substitute(paste(bold("t Dist"))),  cex = 2)
lines(density(t_statistic) , lwd = 2)
abline(v=qt(0.025, df = df), col = "blue")
abline(v=qt(0.975, df = df), col = "blue")
legend("bottom", legend = c("theoretical", "empirical"), col = c("red", "black"), lty = 1, cex = 1, text.font = 2, lwd = 2, bty = "n", ncol=2, inset=c(0, -.22), xpd=TRUE)

# uniform Distribution
plot(z, dt(z, df = df), col = "red",  type = "l", lwd = 2, main = " ", sub = " " , xlab = " ",  ylab = "Density")
title(main = "Density plots of t_18 and U(0,1)", sub = substitute(paste(bold("Uniform Dist"))),  cex = 2)
lines(density(u_statistic) , lwd = 2)
abline(v=qt(0.025, df = df), col = "blue")
abline(v=qt(0.975, df = df), col = "blue")
legend("bottom", legend = c("theoretical", "empirical"), col = c("red", "black"), lty = 1, cex = 1, text.font = 2, lwd = 2, bty = "n", ncol=2, inset=c(0, -.22), xpd=TRUE)

# chi-squared Distribution
plot(z, dt(z, df = df), col = "red",  type = "l", lwd = 2, main = " ", sub = " " , xlab = " ",  ylab = "Density")
title(main = "Density plots of t_18 and Chisq(7)",  sub = substitute(paste(bold("Chi-Square Dist"))),  cex = 2)
lines(density(k_statistic) , lwd = 2)
abline(v=qt(0.025, df = df), col = "blue")
abline(v=qt(0.975, df = df ), col = "blue")
legend("bottom", legend = c("theoretical", "empirical"), col = c("red", "black"), lty = 1, cex = 1, text.font = 2, lwd = 2, bty = "n", ncol=2, inset=c(0, -.22), xpd=TRUE)

# weibull Distribution
plot(z, dt(z, df = df), col = "red" , type = "l", lwd = 2, main = " ", sub = " " , xlab = " ",  ylab = "Density")
title(main = "Density plots of t_18 and Weibull(1, 2)", sub = substitute(paste(bold("Weibull Dist"))),  cex = 2)
lines(density(w_statistic) , lwd = 2)
abline(v=qt(0.025, df = df ), col = "blue")
abline(v=qt(0.975, df = df ), col = "blue")
legend("bottom", legend = c("theoretical", "empirical"), col = c("red", "black"), lty = 1, cex = 1, text.font = 2, lwd = 2, bty = "n", ncol=2, inset=c(0, -.22), xpd=TRUE)

# gamma Distribution
plot(z, dt(z, df = df), col = "red" , type = "l", lwd = 2, main = " ", sub = " " , xlab = " ",  ylab = "Density")
title(main = "Density plots of t_18 and Gamma(3,0.1)", sub = substitute(paste(bold("Gamma Dist"))),  cex = 2)
lines(density(g_statistic) , lwd = 2)
abline(v=qt(0.025, df = df), col = "blue")
abline(v=qt(0.975, df = df), col = "blue")
legend("bottom", legend = c("theoretical", "empirical"), col = c("red", "black"), lty = 1, cex = 1, text.font = 2, lwd = 2, bty = "n", ncol=2, inset=c(0, -.22), xpd=TRUE)

# lognormal Distribution
plot(z, dt(z, df = df), col = "red" , type = "l", lwd = 2, main = " ", sub = " " , xlab = " ",  ylab = "Density")
title(main = "Density plots of t_18 and logN(0,1)", sub = substitute(paste(bold("Lognormal Dist"))),  cex = 2)
lines(density(log_statistic), lwd = 2)
abline(v=qt(0.025, df = df), col = "blue")
abline(v=qt(0.975, df = df), col = "blue")
legend("bottom", legend = c("theoretical ", "empirical"), col = c("red", "black"), lty = 1, cex = 1, text.font = 2, lwd = 3, bty = "n", ncol=2, inset=c(0, -.22), xpd=TRUE)


```

### Normal Distribution
```{r}
df = 2*n - 2
z <- seq(from = -3, to = 3, by = 0.01)
plot(z, dt(z, df = df), col = "red", type = "l", xlab = " ",  ylab = "Density",  lwd = 2, main = " ", sub = " ")
title(main = "Histogram of t test Statistics", sub = "normal Dist")
lines(density(norm_statistic), lwd = 2)
abline(v=qt(0.025, df = df), col = "blue")
abline(v=qt(0.975, df = df), col = "blue")
legend("bottom", legend = c("theoretical t density", "empirical t density"), col = c("red", "black"), lty = 1, cex = 0.75, text.font = 2, lwd = 2, bty = "n", ncol=2, inset=c(0, -.22), xpd=TRUE)
```


### Exponential Distribution
```{r}
plot(z, dt(z, df = df), col = "red",type = "l", lwd = 2, main = " ", sub = " " , xlab = " ",  ylab = "Density")
title(main = "Histogram of t test Statistics", sub = "Exponential Dist")
lines(density(e_statistic) , lwd = 2)
abline(v=qt(0.025, df = df), col = "blue")
abline(v=qt(0.975, df = df), col = "blue")
legend("bottom", legend = c("theoretical t density", "empirical t density"), col = c("red", "black"), lty = 1, cex = 0.75, text.font = 2, lwd = 2, bty = "n", ncol=2, inset=c(0, -.22), xpd=TRUE)
```


### t Distribution
```{r}
plot(z, dt(z, df = df), col = "red", type = "l", lwd = 2, main = " ", sub = " " , xlab = " ",  ylab = "Density")
title(main = "Histogram of t test Statistics", sub = "t Dist")
lines(density(t_statistic) , lwd = 2)
abline(v=qt(0.025, df = df), col = "blue")
abline(v=qt(0.975, df = df), col = "blue")
legend("bottom", legend = c("theoretical t density", "empirical t density"), col = c("red", "black"), lty = 1, cex = 0.75, text.font = 2, lwd = 2, bty = "n", ncol=2, inset=c(0, -.22), xpd=TRUE)
```


### Uniform Distribution
```{r}
plot(z, dt(z, df = df), col = "red",  type = "l", lwd = 2, main = " ", sub = " " , xlab = " ",  ylab = "Density")
title(main = "Histogram of t test Statistics", sub = "Uniform Dist")
lines(density(u_statistic) , lwd = 2)
abline(v=qt(0.025, df = df), col = "blue")
abline(v=qt(0.975, df = df), col = "blue")
legend("bottom", legend = c("theoretical t density", "empirical t density"), col = c("red", "black"), lty = 1, cex = 0.75, text.font = 2, lwd = 2, bty = "n", ncol=2, inset=c(0, -.22), xpd=TRUE)
```


### Chi-Squared Distribution
```{r}
plot(z, dt(z, df = df), col = "red",  type = "l", lwd = 2, main = " ", sub = " " , xlab = " ",  ylab = "Density")
title(main = "Histogram of t test Statistics", sub = "Chi-Square Dist")
lines(density(k_statistic) , lwd = 2)
abline(v=qt(0.025, df = df), col = "blue")
abline(v=qt(0.975, df = df ), col = "blue")
legend("bottom", legend = c("theoretical t density", "empirical t density"), col = c("red", "black"), lty = 1, cex = 0.75, text.font = 2, lwd = 2, bty = "n", ncol=2, inset=c(0, -.22), xpd=TRUE)
```


### Weibull Distribution
```{r}
plot(z, dt(z, df = df), col = "red" , type = "l", lwd = 2, main = " ", sub = " " , xlab = " ",  ylab = "Density")
title(main = "Histogram of t test Statistics", sub = "Weibull Dist")
lines(density(w_statistic) , lwd = 2)
abline(v=qt(0.025, df = df ), col = "blue")
abline(v=qt(0.975, df = df ), col = "blue")
legend("bottom", legend = c("theoretical t density", "empirical t density"), col = c("red", "black"), lty = 1, cex = 0.75, text.font = 2, lwd = 2, bty = "n", ncol=2, inset=c(0, -.22), xpd=TRUE)
```


### gamma Distribution
```{r}
plot(z, dt(z, df = df), col = "red" , type = "l", lwd = 2, main = " ", sub = " " , xlab = " ",  ylab = "Density")
title(main = "Histogram of t test Statistics", sub = "Gamma Dist")
lines(density(g_statistic) , lwd = 2)
abline(v=qt(0.025, df = df), col = "blue")
abline(v=qt(0.975, df = df), col = "blue")
legend("bottom", legend = c("theoretical t density", "empirical t density"), col = c("red", "black"), lty = 1, cex = 0.75, text.font = 2, lwd = 2, bty = "n", ncol=2, inset=c(0, -.22), xpd=TRUE)
```

### Lognormal Distribution
```{r}
plot(z, dt(z, df = n-1), col = "red" , type = "l", lwd = 2, main = " ", sub = " " , xlab = " ",  ylab = "Density")
title(main = "Histogram of t test Statistics", sub = "Lognormal Dist")
lines(density(log_statistic), lwd = 2)
abline(v=qt(0.025, df = df), col = "blue")
abline(v=qt(0.975, df = df), col = "blue")
legend("bottom", legend = c("theoretical t density", "empirical t density"), col = c("red", "black"), lty = 1, cex = 0.75, text.font = 2, lwd = 2, bty = "n", ncol=2, inset=c(0, -.22), xpd=TRUE)
```


```{r}
# Calculation of Type 1 error

#normal Distn
left_norm <- mean(norm_statistic < qt(0.025, df = df))
right_norm <- mean(norm_statistic > qt(0.975, df = df))
Type1_error_norm <- sum(left_norm + right_norm)

#exponential Distn
left_e <- mean(e_statistic < qt(0.025, df = df))
right_e <- mean(e_statistic > qt(0.975, df = df))
Type1_error_e <- sum(left_e + right_e)
#t Distn
left_t <- mean(t_statistic < qt(0.025, df = df))
right_t <- mean(t_statistic > qt(0.975, df = df))
Type1_error_t <- sum(left_t + right_t)
#uuniform Distn
left_u <- mean(u_statistic < qt(0.025, df = df))
right_u <- mean(u_statistic > qt(0.975, df = df))
Type1_error_u <- sum(left_u + right_u)
#Chi-Squared Distn
left_k <- mean(k_statistic < qt(0.025, df = df))
right_k <- mean(k_statistic > qt(0.975, df = df))
Type1_error_k <- sum(left_k + right_k)
#Weilbul Distn
left_w <- mean(w_statistic < qt(0.025, df = df))
right_w <- mean(w_statistic > qt(0.975, df = df))
Type1_error_w <- sum(left_w + right_w)
#Gamma Distn
left_g <- mean(g_statistic < qt(0.025, df = df))
right_g <- mean(g_statistic > qt(0.975, df = df))
Type1_error_g <- sum(left_g + right_g)
#Lognormal Distn
left_l <- mean(log_statistic < qt(0.025, df = df))
right_l <- mean(log_statistic > qt(0.975, df = df))
Type1_error_l <- sum(left_l + right_l)
```

### Estimated Type I errors

```{r}
# Type I error rates
errors <-c( Type1_error_norm, Type1_error_e, Type1_error_t, Type1_error_u,Type1_error_k,Type1_error_w, Type1_error_g,Type1_error_l)
dist <-c("normal", "exponential", "t", "uniform", "chi-squared", "weillbul", "gamma", "lognormal")

# put data in a table
kk <- data.frame(dist, errors)
knitr::kable(kk, caption = "Estimated Type I errors")
```

### Explanation of Results

The theoretical and empirical density plots of the two-sample t test indicates a contrary view to the popular belief that Type I error rates is pronounced for asymmetric distributions like exponential, chi-square, lognormal etc, but controlled for symmetric distributions like normal, uniform, and t. The difference however in the two-sample equal size t test is that Type I error rate is controlled for both symmetric and asymmetric distributions as illustrated in the table above. According to @citekeyposten1978robustness the two sample t-test for equal sample sizes is generally considered to be robust over a wide range of distribution including skewed distributions. Their results showed that the equal-sample size two-sample t-test is relatively robust to departures from normality even more so than most people thought. The authors added that the robustness decreases as the sample size varies more than 10\%. I think this explains why we have a flipped results as shown in the table above.















