---
title: "Utility of Normality Test in Two Samples Test"
author: "Benedict Kongyir"
date: "`r format(Sys.time(), '%m/%d/%Y')`"
output: 
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.height = 8, fig.width = 10)
# Load necessary packages
library(knitr)
library(kableExtra)
```


```{r}
#setwd("/Users/benedictkongyir/Desktop/OSU/Research/Pretest-Simulation/Simulation/AREA UNDER CURVE")
```


### Two Sample Case

```{r}
rm(list = ls())
#load("/Users/benedictkongyir/Desktop/OSU/Research/Results from cluster/TwoSampleAreaUnderCurve_power.RData")

# Power of t-test
Power_ttest <-data.frame(power_t_table)
# Power of Wilcoxon test:
Powerwilcoxtest <-data.frame(power_wilcox_table)
# Power of t_test/wilcoxon test:
Powert_wilcoxtest <-data.frame(power_t_wilcox_table)
# Power of the permutation test:
PowerPermtest <-data.frame(power_perm_table)

# Computation time for t-test 
compTime_ttest <-data.frame(time_t_table)
# Computation time for wilcoxon test
CompTimewilcoxtest <-data.frame(time_wilcox_table)
# Computation time for wilcoxon/ttest
compTime_t_wilcoxtest <-data.frame(time_t_wilcox_table)
# Computation time for permutation test (minutes):
CompTimepermtest <-data.frame(time_perm_table)

```


```{r}
## add extra space to right margin of plot within frame
par(mar = c(7.1, 4.1, 3.1, 6.5), xpd = TRUE)
plot(sample_sizes, Power_ttest$Exponential, axes=FALSE, ylim=c(0,1), xlab="", ylab="", 
     type="o", lwd = 2, col="black", main="Utility of SW test ... Exponential Samples")
lines(sample_sizes, Powerwilcoxtest$Exponential, type = "o", lty = 2, pch = 2, col = "blue", lwd = 3)

axis(2, ylim=c(0,1),col="black",las=1)  
mtext("Power of SW test",side=2,line=2.5)
box()
par(new=TRUE)

## Plot the second plot and put axis scale on right
plot(sample_sizes, compTime_ttest$Exponential,  xlab="", ylab="", ylim=c(0,0.02), 
     axes=FALSE, type="l", lty = 2, lwd = 2, col="red")
lines(sample_sizes, CompTimewilcoxtest$Exponential, type = "o", lty = 2, pch = 2, col = "blue", lwd = 3)
mtext("Inflation of Type I error rate in t test",side=4,col="black",line=4) 
axis(4, ylim=c(0,0.5), col="red",col.axis="black",las=1)
## a little farther out (line=4) to make room for labels
axis(4, ylim=c(0,0.2), col="blue",col.axis="blue",las=1)

## Draw the time axis
axis(1,pretty(range(sample_sizes),10))
mtext("Sample Size",side=1,col="black",line=2.5)  
## Add Legend
legend("bottom", inset = c(0, -0.5), legend=c("power of SW test","Inflation of Type I error"),
       col=c("black","red"), lty = c(1, 2), horiz = TRUE)
```


#### Compare Power of four different test methods
```{r}
#par(mar = c(9, 4, 4, 1), xpd = TRUE)
par(mfrow = c(2,2))
# Adjust margins to reduce space between plots
par(mai = c(0.75, 0.75, 0.2, 0.2))  # Adjust as needed
plot(sample_sizes, Power_ttest$Exponential,  type = "o", lty = 1, pch = 1, col = "red", lwd = 3, 
     ylim = c(0, 1), xlim = range(sample_sizes), xlab = "Sample Size", ylab = "Power")
lines(sample_sizes, Powerwilcoxtest$Exponential, type = "o", lty = 2, pch = 2, col = "blue", lwd = 3)
lines(sample_sizes, Powert_wilcoxtest$Exponential, type = "o", lty = 3, pch = 3, col = "green", lwd = 3)
lines(sample_sizes, PowerPermtest$Exponential, type = "o", lty = 4, pch = 4, col = "orange", lwd = 3)
title(main = "Exponential Samples")
legend("bottomright", legend=c("t","Wilcoxon", "Wilcoxon/ttest", "Permutation"), lwd = 3,
       col=c("red", "blue", "green",  "orange"), lty = 1:4, pch =1:4, cex = 0.8, title = "Test Method")

plot(sample_sizes, Power_ttest$LogNormal, type = "o", lty = 1, pch = 1, col = "red", lwd = 3, 
     ylim = c(0, 1), xlim = range(sample_sizes), xlab = "Sample Size", ylab = "Power")
lines(sample_sizes, Powerwilcoxtest$LogNormal, type = "o", lty = 2, pch = 2, col = "blue", lwd = 3)
lines(sample_sizes, Powert_wilcoxtest$LogNormal, type = "o", lty = 3, pch = 3, col = "green", lwd = 3)
lines(sample_sizes, PowerPermtest$LogNormal, type = "o", lty = 4, pch = 4, col = "orange", lwd = 3)
title(main = "LogNormal Samples")
legend("bottomright", legend=c("t","Wilcoxon", "Wilcoxon/ttes", "Permutation"), lwd = 3,
       col=c("red", "blue", "green",  "orange"), lty = 1:4, pch =1:4, cex = 0.8, title = "Test Method")


plot(sample_sizes, Power_ttest$Chi.Square,  type = "o", lty = 1, pch = 1, col = "red", lwd = 3, 
    ylim = c(0, 1), xlim = range(sample_sizes), xlab = "Sample Size", ylab = "Power")
lines(sample_sizes, Powerwilcoxtest$Chi.Square, type = "o", lty = 2, pch = 2, col = "blue", lwd = 3)
lines(sample_sizes, Powert_wilcoxtest$Chi.Square, type = "o", lty = 3, pch = 3, col = "green", lwd = 3)
lines(sample_sizes, PowerPermtest$Chi.Square, type = "o", lty = 4, pch = 4, col = "orange", lwd = 3)
title(main = "Chi.Square Samples")
legend("bottomright", legend=c("t","Wilcoxon", "Wilcoxon/ttest", "Permutation"), lwd = 3,
       col=c("red", "blue", "green",  "orange"), lty = 1:4, pch =1:4, cex = 0.8, title = "Test Method")

plot(sample_sizes, Power_ttest$Standard.Normal, type = "o", lty = 1, pch = 1, col = "red", lwd = 3, 
   ylim = c(0, 1), xlim = range(sample_sizes), xlab = "Sample Size", ylab = "Power")
lines(sample_sizes, Powerwilcoxtest$Standard.Normal, type = "o", lty = 2, pch = 2, col = "blue", lwd = 3)
lines(sample_sizes, Powert_wilcoxtest$Standard.Normal, type = "o", lty = 3, pch = 3, col = "green", lwd = 3)
lines(sample_sizes, PowerPermtest$Standard.Normal, type = "o", lty = 4, pch = 4, col = "orange", lwd = 3)
title(main = "Standard.Normal Samples")
legend("bottomright", legend=c("t","Wilcoxon", "Wilcoxon/ttest", "Permutation"), lwd = 3,
       col=c("red", "blue", "green",  "orange"), lty = 1:4, pch =1:4, cex = 0.8, title = "Test Method")

```



#### Area Under the Power Curves

```{r}
TestMethod = c("t", "Wilcoxon", "t/Wilcoxon", "Permutation")
Normal = c(0.4242111,  0.4056500, 0.4249556, 0.4252222)
Exponential = c(0.4495222, 0.6531111,  0.6538000, 0.4608444)
ChiSq = c(0.4421722, 0.5754500, 0.5773667, 0.4498111)
LogNormal = c(0.5472611, 0.8531944, 0.8525056, 0.5790111)
# Convert the matrix to a data frame for better display
my_table <- data.frame(TestMethod, Normal, Exponential, ChiSq, LogNormal)
colnames(my_table) <- c("Test Method", "Normal", "Exponential", "Chi-Squared", "LogNormal")
knitr::kable(my_table, caption  = "Area Under the Power Curves")
```


#### Test for Normality using Skewness
```{r}
rm(list = ls())
load("/Users/benedictkongyir/Desktop/OSU/Research/Results from cluster/TwoSampleAreaUnderCurve_Skewness_power.RData")
# Power of t-test
Power_ttest <-data.frame(power_t_table)
# Power of Wilcoxon test:
Powerwilcoxtest <-data.frame(power_wilcox_table)
# Power of t_test/wilcoxon test:
Powert_wilcoxtest <-data.frame(power_t_wilcox_table)
# Power of the permutation test:
PowerPermtest <-data.frame(power_perm_table)

# Computation time for t-test 
compTime_ttest <-data.frame(time_t_table)
# Computation time for wilcoxon test
CompTimewilcoxtest <-data.frame(time_wilcox_table)
# Computation time for wilcoxon/ttest
compTime_t_wilcoxtest <-data.frame(time_t_wilcox_table)
# Computation time for permutation test (minutes):
CompTimepermtest <-data.frame(time_perm_table)

```


```{r}
#par(mar = c(9, 4, 4, 1), xpd = TRUE)
par(mfrow = c(2,2))
# Adjust margins to reduce space between plots
par(mai = c(0.75, 0.75, 0.2, 0.2))  # Adjust as needed
plot(sample_sizes, Power_ttest$Exponential,  type = "o", lty = 1, pch = 1, col = "red", lwd = 3, 
     ylim = c(0, 1), xlim = range(sample_sizes), xlab = "Sample Size", ylab = "Power")
lines(sample_sizes, Powerwilcoxtest$Exponential, type = "o", lty = 2, pch = 2, col = "blue", lwd = 3)
lines(sample_sizes, Powert_wilcoxtest$Exponential, type = "o", lty = 3, pch = 3, col = "green", lwd = 3)
lines(sample_sizes, PowerPermtest$Exponential, type = "o", lty = 4, pch = 4, col = "orange", lwd = 3)
title(main = "Exponential Samples")
legend("bottomright", legend=c("t","Wilcoxon", "Wilcoxon/ttest", "Permutation"), lwd = 3,
       col=c("red", "blue", "green",  "orange"), lty = 1:4, pch =1:4, cex = 0.8, title = "Test Method")

plot(sample_sizes, Power_ttest$LogNormal, type = "o", lty = 1, pch = 1, col = "red", lwd = 3, 
     ylim = c(0, 1), xlim = range(sample_sizes), xlab = "Sample Size", ylab = "Power")
lines(sample_sizes, Powerwilcoxtest$LogNormal, type = "o", lty = 2, pch = 2, col = "blue", lwd = 3)
lines(sample_sizes, Powert_wilcoxtest$LogNormal, type = "o", lty = 3, pch = 3, col = "green", lwd = 3)
lines(sample_sizes, PowerPermtest$LogNormal, type = "o", lty = 4, pch = 4, col = "orange", lwd = 3)
title(main = "LogNormal Samples")
legend("bottomright", legend=c("t","Wilcoxon", "Wilcoxon/ttes", "Permutation"), lwd = 3,
       col=c("red", "blue", "green",  "orange"), lty = 1:4, pch =1:4, cex = 0.8, title = "Test Method")


plot(sample_sizes, Power_ttest$Chi.Square,  type = "o", lty = 1, pch = 1, col = "red", lwd = 3, 
    ylim = c(0, 1), xlim = range(sample_sizes), xlab = "Sample Size", ylab = "Power")
lines(sample_sizes, Powerwilcoxtest$Chi.Square, type = "o", lty = 2, pch = 2, col = "blue", lwd = 3)
lines(sample_sizes, Powert_wilcoxtest$Chi.Square, type = "o", lty = 3, pch = 3, col = "green", lwd = 3)
lines(sample_sizes, PowerPermtest$Chi.Square, type = "o", lty = 4, pch = 4, col = "orange", lwd = 3)
title(main = "Chi.Square Samples")
legend("bottomright", legend=c("t","Wilcoxon", "Wilcoxon/ttest", "Permutation"), lwd = 3,
       col=c("red", "blue", "green",  "orange"), lty = 1:4, pch =1:4, cex = 0.8, title = "Test Method")

plot(sample_sizes, Power_ttest$Standard.Normal, type = "o", lty = 1, pch = 1, col = "red", lwd = 3, 
   ylim = c(0, 1), xlim = range(sample_sizes), xlab = "Sample Size", ylab = "Power")
lines(sample_sizes, Powerwilcoxtest$Standard.Normal, type = "o", lty = 2, pch = 2, col = "blue", lwd = 3)
lines(sample_sizes, Powert_wilcoxtest$Standard.Normal, type = "o", lty = 3, pch = 3, col = "green", lwd = 3)
lines(sample_sizes, PowerPermtest$Standard.Normal, type = "o", lty = 4, pch = 4, col = "orange", lwd = 3)
title(main = "Standard.Normal Samples")
legend("bottomright", legend=c("t","Wilcoxon", "Wilcoxon/ttest", "Permutation"), lwd = 3,
       col=c("red", "blue", "green",  "orange"), lty = 1:4, pch =1:4, cex = 0.8, title = "Test Method")

```


#### Compare Probability of Type I error rates for four Different test methods
```{r}
rm(list = ls())
# load("/Users/benedictkongyir/Desktop/OSU/Research/Pretest-Simulation/COMBINE RESULTS_20240719/COMPARE METHODS/TwoSampleCompareTestMethods_error.RData")
# load("/Users/benedictkongyir/Desktop/OSU/Research/Results from cluster/TwoSampleAreaUnderCurve_error.RData")
load("/Users/benedictkongyir/Desktop/OSU/Research/combined/Latest Codes/COMPARE METHODS/Area Under Curve/ERROR/TwoSampleAreaUnderCurve_error.RData")
# load("/Users/benedictkongyir/Desktop/OSU/Research/Pretest-Simulation/Simulation/AREA UNDER CURVE/TYPE I ERROR/TwoSampleAUCTypeI.errorRate.RData")
# Power of t-test
error_ttest <-data.frame(error_t_table)
# Power of Wilcoxon test:
error_wilcoxtest <-data.frame(error_wilcox_table)
# Power of t_test/wilcoxon test:
error_t_wilcoxtest <-data.frame(error_t_wilcox_table)
# Power of the permutation test:
error_Permtest <-data.frame(error_perm_table)

# # Computation time for t-test 
# compTime_ttest <-data.frame(time_t_table)
# # Computation time for wilcoxon test
# CompTimewilcoxtest <-data.frame(time_wilcox_table)
# # Computation time for wilcoxon/ttest
# compTime_t_wilcoxtest <-data.frame(time_t_wilcox_table)
# # Computation time for permutation test (minutes):
# CompTimepermtest <-data.frame(time_perm_table)

```

```{r}
load("/Users/benedictkongyir/Desktop/OSU/Research/Pretest-Simulation/Simulation/AREA UNDER CURVE/TYPE I ERROR/OneSampleconditionalTypeI_errorRate_04132025.RData")
conditional_error <- data.frame(conditionalTypeI.errorRate)
load("/Users/benedictkongyir/Desktop/OSU/Research/Pretest-Simulation/Simulation/AREA UNDER CURVE/TYPE I ERROR/TwoSampleAUCTypeI_errorRate_04132025.RData")
error_ttest <-data.frame(TypeI.errorRate_t[-1, ])
# Power of Wilcoxon test:
error_wilcoxtest <-data.frame(TypeI.errorRate_wilcox[-1, ])
# Power of t_test/wilcoxon test:
error_t_wilcoxtest <-data.frame(TypeI.errorRate_t_wilcox[-1, ])
error_t_permtest <-data.frame(TypeI.errorRate_t_perm[-1, ])
# Power of the permutation test:
error_Permtest <-data.frame(TypeI.errorRate_perm[-1, ])
```


```{r, fig.height=6, fig.width=12}
par(mfrow = c(1,2))
plot(sample_sizes, conditional_error$Exponential, type = "o", lty = 1, pch = 1, col = "red", lwd = 3, 
     ylim = c(0.02, 0.5), xlim = range(sample_sizes), xlab = "Sample Size", ylab = "Type I error")
lines(sample_sizes, error_ttest$Exponential, type = "o", lty = 2, pch = 2, col = "blue", lwd = 3)

abline(h = 0.05)
title(main = "Conditional vs Unconditional Type I error")
legend("topright", legend=c("conditional","unconditional"), lwd = 3,
       col=c("red", "blue"), lty = 1:2, pch =1:2, cex = 0.8, title = "Test Method")

```


```{r, fig.height=6, fig.width=12}
par(mfrow = c(1,2))
sample_sizes <- sample_sizes[-1]
plot(sample_sizes, error_ttest$Normal, type = "o", lty = 1, pch = 1, col = "red", lwd = 3, 
     ylim = c(0.02, 0.06), xlim = range(sample_sizes), xlab = "Sample Size", ylab = "Type I error")
lines(sample_sizes, error_wilcoxtest$Normal, type = "o", lty = 2, pch = 2, col = "blue", lwd = 3)

lines(sample_sizes, error_Permtest$Normal, type = "o", lty = 3, pch = 3, col = "orange", lwd = 3)
abline(h = 0.05)
title(main = "Normal Samples")
legend("topright", legend=c("t","wilcoxon", "permutation"), lwd = 3,
       col=c("red", "blue",  "orange"), lty = 1:3, pch =1:3, cex = 0.8, title = "Test Method")


plot(sample_sizes, error_ttest$Exponential, type = "o", lty = 1, pch = 1, col = "red", lwd = 3, 
     ylim = c(0.02, 0.06), xlim = range(sample_sizes), xlab = "Sample Size", ylab = "Type I error")
lines(sample_sizes, error_wilcoxtest$Exponential, type = "o", lty = 2, pch = 2, col = "blue", lwd = 3)

lines(sample_sizes, error_Permtest$Exponential, type = "o", lty = 3, pch = 3, col = "orange", lwd = 3)
abline(h = 0.05)
title(main = "Exponential Samples")
legend("topright", legend=c("t","wilcoxon", "permutation"), lwd = 3,
       col=c("red", "blue",  "orange"), lty = 1:3, pch =1:3, cex = 0.8, title = "Test Method")
```


```{r, fig.height=10, fig.width=10}
#par(mar = c(9, 4, 4, 1), xpd = TRUE)
par(mfrow = c(2,2))
# Adjust margins to reduce space between plots
par(mai = c(0.75, 0.75, 0.2, 0.2))  # Adjust as needed
plot(sample_sizes, error_ttest$Exponential,  type = "o", lty = 1, pch = 1, col = "red", lwd = 3, 
     ylim = c(0, 0.1), xlim = range(sample_sizes), xlab = "Sample Size", ylab = "Type I error")
lines(sample_sizes, error_wilcoxtest$Exponential, type = "o", lty = 2, pch = 2, col = "blue", lwd = 3)
lines(sample_sizes, error_t_wilcoxtest$Exponential, type = "o", lty = 3, pch = 3, col = "green", lwd = 3)
lines(sample_sizes, error_Permtest$Exponential, type = "o", lty = 4, pch = 4, col = "orange", lwd = 3)
abline(h = 0.05)
title(main = "Exponential Samples")
legend("bottomright", legend=c("t","Wilcoxon", "Wilcoxon/ttest", "Permutation"), lwd = 3,
       col=c("red", "blue", "green",  "orange"), lty = 1:4, pch =1:4, cex = 0.8, title = "Test Method")

plot(sample_sizes, error_ttest$LogNormal, type = "o", lty = 1, pch = 1, col = "red", lwd = 3, 
     ylim = c(0, 0.1), xlim = range(sample_sizes), xlab = "Sample Size", ylab = "Type I error")
lines(sample_sizes, error_wilcoxtest$LogNormal, type = "o", lty = 2, pch = 2, col = "blue", lwd = 3)
lines(sample_sizes, error_t_wilcoxtest$LogNormal, type = "o", lty = 3, pch = 3, col = "green", lwd = 3)
lines(sample_sizes, error_Permtest$LogNormal, type = "o", lty = 4, pch = 4, col = "orange", lwd = 3)
abline(h = 0.05)
title(main = "LogNormal Samples")
legend("bottomright", legend=c("t","Wilcoxon", "Wilcoxon/ttes", "Permutation"), lwd = 3,
       col=c("red", "blue", "green",  "orange"), lty = 1:4, pch =1:4, cex = 0.8, title = "Test Method")


plot(sample_sizes, error_ttest$Chi.Square,  type = "o", lty = 1, pch = 1, col = "red", lwd = 3, 
    ylim = c(0, 0.1), xlim = range(sample_sizes), xlab = "Sample Size", ylab = "Type I error")
lines(sample_sizes, error_wilcoxtest$Chi.Square, type = "o", lty = 2, pch = 2, col = "blue", lwd = 3)
lines(sample_sizes, error_t_wilcoxtest$Chi.Square, type = "o", lty = 3, pch = 3, col = "green", lwd = 3)
lines(sample_sizes, error_Permtest$Chi.Square, type = "o", lty = 4, pch = 4, col = "orange", lwd = 3)
abline(h = 0.05)
title(main = "Chi.Square Samples")
legend("bottomright", legend=c("t","Wilcoxon", "Wilcoxon/ttest", "Permutation"), lwd = 3,
       col=c("red", "blue", "green",  "orange"), lty = 1:4, pch =1:4, cex = 0.8, title = "Test Method")

plot(sample_sizes, error_ttest$Standard.Normal, type = "o", lty = 1, pch = 1, col = "red", lwd = 3, 
   ylim = c(0, 0.1), xlim = range(sample_sizes), xlab = "Sample Size", ylab = "Type I error")
lines(sample_sizes, error_wilcoxtest$Standard.Normal, type = "o", lty = 2, pch = 2, col = "blue", lwd = 3)
lines(sample_sizes, error_t_wilcoxtest$Standard.Normal, type = "o", lty = 3, pch = 3, col = "green", lwd = 3)
lines(sample_sizes, error_Permtest$Standard.Normal, type = "o", lty = 4, pch = 4, col = "orange", lwd = 3)
abline(h = 0.05)
title(main = "Standard.Normal Samples")
legend("bottomright", legend=c("t","Wilcoxon", "Wilcoxon/ttest", "Permutation"), lwd = 3,
       col=c("red", "blue", "green",  "orange"), lty = 1:4, pch =1:4, cex = 0.8, title = "Test Method")

```

#### Area Under the error Curves

```{r}
TestMethod = c("t", "Wilcoxon", "t/Wilcoxon", "Permutation")
Normal = c(-0.000200 ,  -0.00171 , -0.00167 , 0.000285)
Exponential = c( -0.005895 ,  -0.00314 ,   -0.00314,  -0.000665 )
ChiSq = c( -0.003545 ,  -0.00260 ,  -0.00260 ,  -0.000420  )
LogNormal = c( -0.013060 ,  -0.00222 , -0.00222,   -0.000495 )
# Convert the matrix to a data frame for better display
my_table <- data.frame(TestMethod, Normal, Exponential, ChiSq, LogNormal)
colnames(my_table) <- c("Test Method", "Normal", "Exponential", "Chi-Squared", "LogNormal")
knitr::kable(my_table, caption  = "Area Under the Type I error rate Curves")
```



### Skewness Method

#### Compare Probability of Type I error rates for four Different test methods
```{r}
rm(list = ls())
load("/Users/benedictkongyir/Desktop/OSU/Research/Results from cluster/TwoSampleAreaUnderCurveSkewness_error.RData")
# Power of t-test
error_ttest <-data.frame(error_t_table)
# Power of Wilcoxon test:
error_wilcoxtest <-data.frame(error_wilcox_table)
# Power of t_test/wilcoxon test:
error_t_wilcoxtest <-data.frame(error_t_wilcox_table)
# Power of the permutation test:
error_Permtest <-data.frame(error_perm_table)

# Computation time for t-test 
compTime_ttest <-data.frame(time_t_table)
# Computation time for wilcoxon test
CompTimewilcoxtest <-data.frame(time_wilcox_table)
# Computation time for wilcoxon/ttest
compTime_t_wilcoxtest <-data.frame(time_t_wilcox_table)
# Computation time for permutation test (minutes):
CompTimepermtest <-data.frame(time_perm_table)

```


```{r}
#par(mar = c(9, 4, 4, 1), xpd = TRUE)
par(mfrow = c(2,2))
# Adjust margins to reduce space between plots
par(mai = c(0.75, 0.75, 0.2, 0.2))  # Adjust as needed
plot(sample_sizes, error_ttest$Exponential,  type = "o", lty = 1, pch = 1, col = "red", lwd = 3, 
     ylim = c(0, 0.1), xlim = range(sample_sizes), xlab = "Sample Size", ylab = "Type I error")
lines(sample_sizes, error_wilcoxtest$Exponential, type = "o", lty = 2, pch = 2, col = "blue", lwd = 3)
lines(sample_sizes, error_t_wilcoxtest$Exponential, type = "o", lty = 3, pch = 3, col = "green", lwd = 3)
lines(sample_sizes, error_Permtest$Exponential, type = "o", lty = 4, pch = 4, col = "orange", lwd = 3)
abline(h = 0.05)
title(main = "Exponential Samples")
legend("bottomright", legend=c("t","Wilcoxon", "Wilcoxon/ttest", "Permutation"), lwd = 3,
       col=c("red", "blue", "green",  "orange"), lty = 1:4, pch =1:4, cex = 0.8, title = "Test Method")

plot(sample_sizes, error_ttest$LogNormal, type = "o", lty = 1, pch = 1, col = "red", lwd = 3, 
     ylim = c(0, 0.1), xlim = range(sample_sizes), xlab = "Sample Size", ylab = "Type I error")
lines(sample_sizes, error_wilcoxtest$LogNormal, type = "o", lty = 2, pch = 2, col = "blue", lwd = 3)
lines(sample_sizes, error_t_wilcoxtest$LogNormal, type = "o", lty = 3, pch = 3, col = "green", lwd = 3)
lines(sample_sizes, error_Permtest$LogNormal, type = "o", lty = 4, pch = 4, col = "orange", lwd = 3)
abline(h = 0.05)
title(main = "LogNormal Samples")
legend("bottomright", legend=c("t","Wilcoxon", "Wilcoxon/ttes", "Permutation"), lwd = 3,
       col=c("red", "blue", "green",  "orange"), lty = 1:4, pch =1:4, cex = 0.8, title = "Test Method")


plot(sample_sizes, error_ttest$Chi.Square,  type = "o", lty = 1, pch = 1, col = "red", lwd = 3, 
    ylim = c(0, 0.1), xlim = range(sample_sizes), xlab = "Sample Size", ylab = "Type I error")
lines(sample_sizes, error_wilcoxtest$Chi.Square, type = "o", lty = 2, pch = 2, col = "blue", lwd = 3)
lines(sample_sizes, error_t_wilcoxtest$Chi.Square, type = "o", lty = 3, pch = 3, col = "green", lwd = 3)
lines(sample_sizes, error_Permtest$Chi.Square, type = "o", lty = 4, pch = 4, col = "orange", lwd = 3)
abline(h = 0.05)
title(main = "Chi.Square Samples")
legend("bottomright", legend=c("t","Wilcoxon", "Wilcoxon/ttest", "Permutation"), lwd = 3,
       col=c("red", "blue", "green",  "orange"), lty = 1:4, pch =1:4, cex = 0.8, title = "Test Method")

plot(sample_sizes, error_ttest$Standard.Normal, type = "o", lty = 1, pch = 1, col = "red", lwd = 3, 
   ylim = c(0, 0.1), xlim = range(sample_sizes), xlab = "Sample Size", ylab = "Type I error")
lines(sample_sizes, error_wilcoxtest$Standard.Normal, type = "o", lty = 2, pch = 2, col = "blue", lwd = 3)
lines(sample_sizes, error_t_wilcoxtest$Standard.Normal, type = "o", lty = 3, pch = 3, col = "green", lwd = 3)
lines(sample_sizes, error_Permtest$Standard.Normal, type = "o", lty = 4, pch = 4, col = "orange", lwd = 3)
abline(h = 0.05)
title(main = "Standard.Normal Samples")
legend("bottomright", legend=c("t","Wilcoxon", "Wilcoxon/ttest", "Permutation"), lwd = 3,
       col=c("red", "blue", "green",  "orange"), lty = 1:4, pch =1:4, cex = 0.8, title = "Test Method")

```






### One Sample Case Power

```{r}
rm(list = ls())
#load("/Users/benedictkongyir/Desktop/OSU/Research/Pretest-Simulation/COMBINE RESULTS_20240719/COMPARE METHODS/OneSampleCompareTestMethods_power.RData")
load("/Users/benedictkongyir/Desktop/OSU/Research/Results from cluster/OneSampleAreaUnderCurve_power.RData")
# Power of t-test
Power_ttest <-data.frame(power_t_table)
# Power of Wilcoxon test:
Powerwilcoxtest <-data.frame(power_wilcox_table)
# Power of t_test/wilcoxon test:
Powert_wilcoxtest <-data.frame(power_t_wilcox_table)
# Power of the permutation test:
PowerPermtest <-data.frame(power_perm_table)

# Computation time for t-test 
compTime_ttest <-data.frame(time_t_table)
# Computation time for wilcoxon test
CompTimewilcoxtest <-data.frame(time_wilcox_table)
# Computation time for wilcoxon/ttest
compTime_ttest <-data.frame(time_t_wilcox_table)
# Computation time for permutation test (minutes):
CompTimewilcoxtest <-data.frame(time_perm_table)

```

#### Power of t-test/Mann-Whitney U test vs. permutation test
```{r}
#par(mar = c(9, 4, 4, 1), xpd = TRUE)
par(mfrow = c(2,2))
# Adjust margins to reduce space between plots
par(mai = c(0.75, 0.75, 0.2, 0.2))  # Adjust as needed
plot(sample_sizes, Power_ttest$Exponential,  type = "o", lty = 1, pch = 1, col = "red", lwd = 3, 
     ylim = c(0, 1), xlim = range(sample_sizes), xlab = "Sample Size", ylab = "Power")
lines(sample_sizes, Powerwilcoxtest$Exponential, type = "o", lty = 2, pch = 2, col = "blue", lwd = 3)
lines(sample_sizes, Powert_wilcoxtest$Exponential, type = "o", lty = 3, pch = 3, col = "green", lwd = 3)
lines(sample_sizes, PowerPermtest$Exponential, type = "o", lty = 4, pch = 4, col = "orange", lwd = 3)
title(main = "Exponential Samples")
legend("bottomright", legend=c("t","Wilcoxon", "Wilcoxon/ttest", "Permutation"), lwd = 3,
       col=c("red", "blue", "green",  "orange"), lty = 1:4, pch =1:4, cex = 0.8, title = "Test Method")

plot(sample_sizes, Power_ttest$LogNormal, type = "o", lty = 1, pch = 1, col = "red", lwd = 3, 
     ylim = c(0, 1), xlim = range(sample_sizes), xlab = "Sample Size", ylab = "Power")
lines(sample_sizes, Powerwilcoxtest$LogNormal, type = "o", lty = 2, pch = 2, col = "blue", lwd = 3)
lines(sample_sizes, Powert_wilcoxtest$LogNormal, type = "o", lty = 3, pch = 3, col = "green", lwd = 3)
lines(sample_sizes, PowerPermtest$LogNormal, type = "o", lty = 4, pch = 4, col = "orange", lwd = 3)
title(main = "LogNormal Samples")
legend("bottomright", legend=c("t","Wilcoxon", "Wilcoxon/ttes", "Permutation"), lwd = 3,
       col=c("red", "blue", "green",  "orange"), lty = 1:4, pch =1:4, cex = 0.8, title = "Test Method")


plot(sample_sizes, Power_ttest$Chi.Square,  type = "o", lty = 1, pch = 1, col = "red", lwd = 3, 
    ylim = c(0, 1), xlim = range(sample_sizes), xlab = "Sample Size", ylab = "Power")
lines(sample_sizes, Powerwilcoxtest$Chi.Square, type = "o", lty = 2, pch = 2, col = "blue", lwd = 3)
lines(sample_sizes, Powert_wilcoxtest$Chi.Square, type = "o", lty = 3, pch = 3, col = "green", lwd = 3)
lines(sample_sizes, PowerPermtest$Chi.Square, type = "o", lty = 4, pch = 4, col = "orange", lwd = 3)
title(main = "Chi.Square Samples")
legend("bottomright", legend=c("t","Wilcoxon", "Wilcoxon/ttest", "Permutation"), lwd = 3,
       col=c("red", "blue", "green",  "orange"), lty = 1:4, pch =1:4, cex = 0.8, title = "Test Method")

plot(sample_sizes, Power_ttest$Standard.Normal, type = "o", lty = 1, pch = 1, col = "red", lwd = 3, 
   ylim = c(0, 1), xlim = range(sample_sizes), xlab = "Sample Size", ylab = "Power")
lines(sample_sizes, Powerwilcoxtest$Standard.Normal, type = "o", lty = 2, pch = 2, col = "blue", lwd = 3)
lines(sample_sizes, Powert_wilcoxtest$Standard.Normal, type = "o", lty = 3, pch = 3, col = "green", lwd = 3)
lines(sample_sizes, PowerPermtest$Standard.Normal, type = "o", lty = 4, pch = 4, col = "orange", lwd = 3)
title(main = "Standard.Normal Samples")
legend("bottomright", legend=c("t","Wilcoxon", "Wilcoxon/ttest", "Permutation"), lwd = 3,
       col=c("red", "blue", "green",  "orange"), lty = 1:4, pch =1:4, cex = 0.8, title = "Test Method")

```


#### Area Under the Power Curves

```{r}
TestMethod = c("t", "Wilcoxon", "t/Wilcoxon", "Permutation")
Normal = c(0.6461000,  0.6213111, 0.6453611, 0.6375000)
Exponential = c(0.6819111, 0.5300722,  0.5431833, 0.7062278)
ChiSq = c(0.6682056, 0.5359500, 0.5565056, 0.6833167)
LogNormal = c(0.8059889, 0.8222889, 0.8309278, 0.8747333)
# Convert the matrix to a data frame for better display
my_table <- data.frame(TestMethod, Normal, Exponential, ChiSq, LogNormal)
colnames(my_table) <- c("Test Method", "Normal", "Exponential", "Chi-Squared", "LogNormal")
knitr::kable(my_table, caption  = "Area Under the Power Curves")
```


```{r}
rm(list = ls())
load("/Users/benedictkongyir/Desktop/OSU/Research/Results from cluster/OneSampleAreaUnderCurve_Skewness_power.RData")
# Power of t-test
Power_ttest <-data.frame(power_t_table)
# Power of Wilcoxon test:
Powerwilcoxtest <-data.frame(power_wilcox_table)
# Power of t_test/wilcoxon test:
Powert_wilcoxtest <-data.frame(power_t_wilcox_table)
# Power of the permutation test:
PowerPermtest <-data.frame(power_perm_table)

# Computation time for t-test 
compTime_ttest <-data.frame(time_t_table)
# Computation time for wilcoxon test
CompTimewilcoxtest <-data.frame(time_wilcox_table)
# Computation time for wilcoxon/ttest
compTime_ttest <-data.frame(time_t_wilcox_table)
# Computation time for permutation test (minutes):
CompTimewilcoxtest <-data.frame(time_perm_table)

```

#### Skewness Method
```{r}
#par(mar = c(9, 4, 4, 1), xpd = TRUE)
par(mfrow = c(2,2))
# Adjust margins to reduce space between plots
par(mai = c(0.75, 0.75, 0.2, 0.2))  # Adjust as needed
plot(sample_sizes, Power_ttest$Exponential,  type = "o", lty = 1, pch = 1, col = "red", lwd = 3, 
     ylim = c(0, 1), xlim = range(sample_sizes), xlab = "Sample Size", ylab = "Power")
lines(sample_sizes, Powerwilcoxtest$Exponential, type = "o", lty = 2, pch = 2, col = "blue", lwd = 3)
lines(sample_sizes, Powert_wilcoxtest$Exponential, type = "o", lty = 3, pch = 3, col = "green", lwd = 3)
lines(sample_sizes, PowerPermtest$Exponential, type = "o", lty = 4, pch = 4, col = "orange", lwd = 3)
title(main = "Exponential Samples")
legend("bottomright", legend=c("t","Wilcoxon", "Wilcoxon/ttest", "Permutation"), lwd = 3,
       col=c("red", "blue", "green",  "orange"), lty = 1:4, pch =1:4, cex = 0.8, title = "Test Method")

plot(sample_sizes, Power_ttest$LogNormal, type = "o", lty = 1, pch = 1, col = "red", lwd = 3, 
     ylim = c(0, 1), xlim = range(sample_sizes), xlab = "Sample Size", ylab = "Power")
lines(sample_sizes, Powerwilcoxtest$LogNormal, type = "o", lty = 2, pch = 2, col = "blue", lwd = 3)
lines(sample_sizes, Powert_wilcoxtest$LogNormal, type = "o", lty = 3, pch = 3, col = "green", lwd = 3)
lines(sample_sizes, PowerPermtest$LogNormal, type = "o", lty = 4, pch = 4, col = "orange", lwd = 3)
title(main = "LogNormal Samples")
legend("bottomright", legend=c("t","Wilcoxon", "Wilcoxon/ttes", "Permutation"), lwd = 3,
       col=c("red", "blue", "green",  "orange"), lty = 1:4, pch =1:4, cex = 0.8, title = "Test Method")


plot(sample_sizes, Power_ttest$Chi.Square,  type = "o", lty = 1, pch = 1, col = "red", lwd = 3, 
    ylim = c(0, 1), xlim = range(sample_sizes), xlab = "Sample Size", ylab = "Power")
lines(sample_sizes, Powerwilcoxtest$Chi.Square, type = "o", lty = 2, pch = 2, col = "blue", lwd = 3)
lines(sample_sizes, Powert_wilcoxtest$Chi.Square, type = "o", lty = 3, pch = 3, col = "green", lwd = 3)
lines(sample_sizes, PowerPermtest$Chi.Square, type = "o", lty = 4, pch = 4, col = "orange", lwd = 3)
title(main = "Chi.Square Samples")
legend("bottomright", legend=c("t","Wilcoxon", "Wilcoxon/ttest", "Permutation"), lwd = 3,
       col=c("red", "blue", "green",  "orange"), lty = 1:4, pch =1:4, cex = 0.8, title = "Test Method")

plot(sample_sizes, Power_ttest$Standard.Normal, type = "o", lty = 1, pch = 1, col = "red", lwd = 3, 
   ylim = c(0, 1), xlim = range(sample_sizes), xlab = "Sample Size", ylab = "Power")
lines(sample_sizes, Powerwilcoxtest$Standard.Normal, type = "o", lty = 2, pch = 2, col = "blue", lwd = 3)
lines(sample_sizes, Powert_wilcoxtest$Standard.Normal, type = "o", lty = 3, pch = 3, col = "green", lwd = 3)
lines(sample_sizes, PowerPermtest$Standard.Normal, type = "o", lty = 4, pch = 4, col = "orange", lwd = 3)
title(main = "Standard.Normal Samples")
legend("bottomright", legend=c("t","Wilcoxon", "Wilcoxon/ttest", "Permutation"), lwd = 3,
       col=c("red", "blue", "green",  "orange"), lty = 1:4, pch =1:4, cex = 0.8, title = "Test Method")

```





#### Probability of Type I error rates
```{r}
rm(list = ls())
#load("/Users/benedictkongyir/Desktop/OSU/Research/Pretest-Simulation/COMBINE RESULTS_20240719/COMPARE METHODS/OneampleCompareTestMethods_error.RData")
load("/Users/benedictkongyir/Desktop/OSU/Research/Results from cluster/OneSampleAreaUnderCurve_error.RData")
# Power of t-test
error_ttest <-data.frame(error_t_table)
# Power of Wilcoxon test:
error_wilcoxtest <-data.frame(error_wilcox_table)
# Power of t_test/wilcoxon test:
error_t_wilcoxtest <-data.frame(error_t_wilcox_table)
# Power of the permutation test:
error_Permtest <-data.frame(error_perm_table)

# Computation time for t-test 
compTime_ttest <-data.frame(time_t_table)
# Computation time for wilcoxon test
CompTimewilcoxtest <-data.frame(time_wilcox_table)
# Computation time for wilcoxon/ttest
compTime_t_wilcoxtest <-data.frame(time_t_wilcox_table)
# Computation time for permutation test (minutes):
CompTimepermtest <-data.frame(time_perm_table)

```

#### Power of t-test/Mann-Whitney U test vs. permutation test
```{r}
#par(mar = c(9, 4, 4, 1), xpd = TRUE)
par(mfrow = c(2,2))
# Adjust margins to reduce space between plots
par(mai = c(0.75, 0.75, 0.2, 0.2))  # Adjust as needed
plot(sample_sizes, error_ttest$Exponential,  type = "o", lty = 1, pch = 1, col = "red", lwd = 3, 
     ylim = c(0, 0.5), xlim = range(sample_sizes), xlab = "Sample Size", ylab = "Type I error")
lines(sample_sizes, error_wilcoxtest$Exponential, type = "o", lty = 2, pch = 2, col = "blue", lwd = 3)
lines(sample_sizes, error_t_wilcoxtest$Exponential, type = "o", lty = 3, pch = 3, col = "green", lwd = 3)
lines(sample_sizes, error_Permtest$Exponential, type = "o", lty = 4, pch = 4, col = "orange", lwd = 3)
abline(h = 0.05)
title(main = "Exponential Samples")
legend("topleft", legend=c("t","Wilcoxon", "Wilcoxon/ttest", "Permutation"), lwd = 3,
       col=c("red", "blue", "green",  "orange"), lty = 1:4, pch =1:4, cex = 0.8, title = "Test Method")

plot(sample_sizes, error_ttest$LogNormal, type = "o", lty = 1, pch = 1, col = "red", lwd = 3, 
     ylim = c(0, 0.5), xlim = range(sample_sizes), xlab = "Sample Size", ylab = "Type I error")
lines(sample_sizes, error_wilcoxtest$LogNormal, type = "o", lty = 2, pch = 2, col = "blue", lwd = 3)
lines(sample_sizes, error_t_wilcoxtest$LogNormal, type = "o", lty = 3, pch = 3, col = "green", lwd = 3)
lines(sample_sizes, error_Permtest$LogNormal, type = "o", lty = 4, pch = 4, col = "orange", lwd = 3)
abline(h = 0.05)
title(main = "LogNormal Samples")
legend("topleft", legend=c("t","Wilcoxon", "Wilcoxon/ttes", "Permutation"), lwd = 3,
       col=c("red", "blue", "green",  "orange"), lty = 1:4, pch =1:4, cex = 0.8, title = "Test Method")


plot(sample_sizes, error_ttest$Chi.Square,  type = "o", lty = 1, pch = 1, col = "red", lwd = 3, 
    ylim = c(0, 0.5), xlim = range(sample_sizes), xlab = "Sample Size", ylab = "Type I error")
lines(sample_sizes, error_wilcoxtest$Chi.Square, type = "o", lty = 2, pch = 2, col = "blue", lwd = 3)
lines(sample_sizes, error_t_wilcoxtest$Chi.Square, type = "o", lty = 3, pch = 3, col = "green", lwd = 3)
lines(sample_sizes, error_Permtest$Chi.Square, type = "o", lty = 4, pch = 4, col = "orange", lwd = 3)
abline(h = 0.05)
title(main = "Chi.Square Samples")
legend("topleft", legend=c("t","Wilcoxon", "Wilcoxon/ttest", "Permutation"), lwd = 3,
       col=c("red", "blue", "green",  "orange"), lty = 1:4, pch =1:4, cex = 0.8, title = "Test Method")

plot(sample_sizes, error_ttest$Standard.Normal, type = "o", lty = 1, pch = 1, col = "red", lwd = 3, 
   ylim = c(0, 0.5), xlim = range(sample_sizes), xlab = "Sample Size", ylab = "Type I error")
lines(sample_sizes, error_wilcoxtest$Standard.Normal, type = "o", lty = 2, pch = 2, col = "blue", lwd = 3)
lines(sample_sizes, error_t_wilcoxtest$Standard.Normal, type = "o", lty = 3, pch = 3, col = "green", lwd = 3)
lines(sample_sizes, error_Permtest$Standard.Normal, type = "o", lty = 4, pch = 4, col = "orange", lwd = 3)
abline(h = 0.05)
title(main = "Standard.Normal Samples")
legend("topleft", legend=c("t","Wilcoxon", "Wilcoxon/ttest", "Permutation"), lwd = 3,
       col=c("red", "blue", "green",  "orange"), lty = 1:4, pch =1:4, cex = 0.8, title = "Test Method")

```


#### Area Under the Type I error rate Curves
```{r}
TestMethod = c("t", "Wilcoxon", "t/Wilcoxon", "Permutation")
Normal = c(0.00050,  -0.00280, 0.00220, -0.00215)
Exponential = c(0.02800, 0.09155,  0.09670, 0.02215)
ChiSq = c(0.01645, 0.05765, 0.06330, 0.01075)
LogNormal = c(0.07725, 0.23725, 0.24595, 0.06860)
# Convert the matrix to a data frame for better display
my_table <- data.frame(TestMethod, Normal, Exponential, ChiSq, LogNormal)
colnames(my_table) <- c("Test Method", "Normal", "Exponential", "Chi-Squared", "LogNormal")
knitr::kable(my_table, caption  = "Area Under the Type I error rate Curves")
```



#### Skewness Method
```{r}
rm(list = ls())
load("/Users/benedictkongyir/Desktop/OSU/Research/Results from cluster/OneSampleAreaUnderCurveSkewness_error.RData")
# error of t-test
error_ttest <-data.frame(error_t_table)
# error of Wilcoxon test:
error_wilcoxtest <-data.frame(error_wilcox_table)
# error of t_test/wilcoxon test:
error_t_wilcoxtest <-data.frame(error_t_wilcox_table)
# error of the permutation test:
error_Permtest <-data.frame(error_perm_table)

# Computation time for t-test 
compTime_ttest <-data.frame(time_t_table)
# Computation time for wilcoxon test
CompTimewilcoxtest <-data.frame(time_wilcox_table)
# Computation time for wilcoxon/ttest
compTime_t_wilcoxtest <-data.frame(time_t_wilcox_table)
# Computation time for permutation test (minutes):
CompTimepermtest <-data.frame(time_perm_table)

```

#### Type I error of t-test/Mann-Whitney U test vs. permutation test
```{r}
#par(mar = c(9, 4, 4, 1), xpd = TRUE)
par(mfrow = c(2,2))
# Adjust margins to reduce space between plots
par(mai = c(0.75, 0.75, 0.2, 0.2))  # Adjust as needed
plot(sample_sizes, error_ttest$Exponential,  type = "o", lty = 1, pch = 1, col = "red", lwd = 3, 
     ylim = c(0, 0.5), xlim = range(sample_sizes), xlab = "Sample Size", ylab = "Power")
lines(sample_sizes, error_wilcoxtest$Exponential, type = "o", lty = 2, pch = 2, col = "blue", lwd = 3)
lines(sample_sizes, error_t_wilcoxtest$Exponential, type = "o", lty = 3, pch = 3, col = "green", lwd = 3)
lines(sample_sizes, error_Permtest$Exponential, type = "o", lty = 4, pch = 4, col = "orange", lwd = 3)
abline(h = 0.05)
title(main = "Exponential Samples")
legend("topleft", legend=c("t","Wilcoxon", "Wilcoxon/ttest", "Permutation"), lwd = 3,
       col=c("red", "blue", "green",  "orange"), lty = 1:4, pch =1:4, cex = 0.8, title = "Test Method")

plot(sample_sizes, error_ttest$LogNormal, type = "o", lty = 1, pch = 1, col = "red", lwd = 3, 
     ylim = c(0, 0.5), xlim = range(sample_sizes), xlab = "Sample Size", ylab = "Power")
lines(sample_sizes, error_wilcoxtest$LogNormal, type = "o", lty = 2, pch = 2, col = "blue", lwd = 3)
lines(sample_sizes, error_t_wilcoxtest$LogNormal, type = "o", lty = 3, pch = 3, col = "green", lwd = 3)
lines(sample_sizes, error_Permtest$LogNormal, type = "o", lty = 4, pch = 4, col = "orange", lwd = 3)
abline(h = 0.05)
title(main = "LogNormal Samples")
legend("topleft", legend=c("t","Wilcoxon", "Wilcoxon/ttes", "Permutation"), lwd = 3,
       col=c("red", "blue", "green",  "orange"), lty = 1:4, pch =1:4, cex = 0.8, title = "Test Method")


plot(sample_sizes, error_ttest$Chi.Square,  type = "o", lty = 1, pch = 1, col = "red", lwd = 3, 
    ylim = c(0, 0.5), xlim = range(sample_sizes), xlab = "Sample Size", ylab = "Power")
lines(sample_sizes, error_wilcoxtest$Chi.Square, type = "o", lty = 2, pch = 2, col = "blue", lwd = 3)
lines(sample_sizes, error_t_wilcoxtest$Chi.Square, type = "o", lty = 3, pch = 3, col = "green", lwd = 3)
lines(sample_sizes, error_Permtest$Chi.Square, type = "o", lty = 4, pch = 4, col = "orange", lwd = 3)
abline(h = 0.05)
title(main = "Chi.Square Samples")
legend("topleft", legend=c("t","Wilcoxon", "Wilcoxon/ttest", "Permutation"), lwd = 3,
       col=c("red", "blue", "green",  "orange"), lty = 1:4, pch =1:4, cex = 0.8, title = "Test Method")

plot(sample_sizes, error_ttest$Standard.Normal, type = "o", lty = 1, pch = 1, col = "red", lwd = 3, 
   ylim = c(0, 0.5), xlim = range(sample_sizes), xlab = "Sample Size", ylab = "Power")
lines(sample_sizes, error_wilcoxtest$Standard.Normal, type = "o", lty = 2, pch = 2, col = "blue", lwd = 3)
lines(sample_sizes, error_t_wilcoxtest$Standard.Normal, type = "o", lty = 3, pch = 3, col = "green", lwd = 3)
lines(sample_sizes, error_Permtest$Standard.Normal, type = "o", lty = 4, pch = 4, col = "orange", lwd = 3)
abline(h = 0.05)
title(main = "Standard.Normal Samples")
legend("topleft", legend=c("t","Wilcoxon", "Wilcoxon/ttest", "Permutation"), lwd = 3,
       col=c("red", "blue", "green",  "orange"), lty = 1:4, pch =1:4, cex = 0.8, title = "Test Method")

```







